### 2021-09-17 products/manuscript/Manuscript.Rmd
.

---
title: "Example Manuscript Template for a Data Analysis Project"
subtitle: ""
author: Andreas Handel
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: article
output:
  bookdown::word_document2: 
    toc: false
    number_sections: true
  bookdown::html_document2: 
    toc: false
bibliography: ../references.bib
csl: ../apa.csl
---

The structure below is a possible setup for a data analysis project (including the course project). For a manuscript, adjust as needed.

# Summary/Abstract
_Write a summary of your project._

# Introduction

## General Background Information
During the COVID-19 pandemic, the government of Bangladesh adopted nationwide lockdown. There has been some studies that showed its adverse  effect on people of Bangladesh. As the government has taken the vaccination program very strictly, it was expected to see a large number of population would get vaccinated. But as the reality was the opposite, we wanted to know why people are not getting vaccinated enough despite being affected by COVID-19 lockdown. Our research will shed somelight on Bangladeshi people's vaccine hesitancy. Als briefly, out work will present its relation to mental wellness.

## Description of data and data source
Data was/will be collected using online questionnaire.

## Questions/Hypotheses to be addressed
The main question is to find out why people gets hesitant to get vaccinated. Finding out their key motivator is the prime goal. Also, how mental wellness after covid-19 lockdown might affect their hesitant desition to get vaccinated, is another question we want to answer.

[I still haven't got access to the data. As soon as I get access to the data, I can update more information like how many subjects were included and info like that.]

# Methods and Results

_In most research papers, results and methods are separate. You can combine them here if you find it easier. You are also welcome to structure things such that those are separate sections._

## Data aquisition
_As applicable, explain where and how you got the data. If you directly import the data from an online source, you can combine this section with the next._

## Data import and cleaning
_Write code that reads in the file and cleans it so it's ready for analysis. Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts. If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g. as supplement in a paper). All materials, including files that contain code, should be commented well so everyone can follow along._

## Exploratory analysis

_Use a combination of text/tables/figures to explore and describe your data. You should produce plots or tables or other summary quantities for the most interesting/important quantities in your data. Depending on the total number of variables in your dataset, explore all or some of the others. FIgures produced here might be histograms or density plots, correlation plots, etc. Tables might summarize your data._

_Continue by creating plots or tables of the outcome(s) of interest and the predictor/exposure/input variables you are most interested in. If your dataset is small, you can do that for all variables. Plots produced here can be scatterplots, boxplots, violinplots, etc. Tables can be simple 2x2 tables or larger ones._

_To get some further insight into your data, if reasonable you could compute simple statistics (e.g. t-tests, simple regression model with 1 predictor, etc.) to look for associations between your outcome(s) and each individual predictor variable. Though note that unless you pre-specified the outcome and main exposure, any "p<0.05 means statistical significance" interpretation is not valid._

Table \@ref(tab:summarytable) shows a table summarizing the data.

```{r summarytable,  echo=FALSE}
resulttable=readRDS("../../results/summarytable.rds")
knitr::kable(resulttable, caption = 'Data summary table.')
```

Figure \@ref(fig:resultfigure) shows a scatterplot figure produced by one of the R scripts.

```{r resultfigure,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/resultfigure.png")
```

## Full analysis

_Use one or several suitable statistical/machine learning methods to analyze your data and to produce meaningful figures, tables, etc. This might again be code that is best placed in one or several separate R scripts that need to be well documented. You want the code to produce figures and data ready for display as tables, and save those. Then you load them here._

Example table \@ref(tab:resulttable) shows a table summarizing a linear model fit.

```{r resulttable,  echo=FALSE}
resulttable=readRDS("../../results/resulttable.rds")
knitr::kable(resulttable, caption = 'Linear model fit table.')
```

# Discussion

## Summary and Interpretation
_Summarize what you did, what you found and what it means._

## Strengths and Limitations
_Discuss what you perceive as strengths and limitations of your analysis._

## Conclusions
_What are the main take-home messages?_

_Include citations in your Rmd file using bibtex, the list of references will automatically be placed at the end_

This paper [@Leek2015a] discusses types of analyses.

Note that this cited reference will show up at the end of the document, the reference formatting is determined by the CSL file specified in the YAML header. Many more style files for almost any journal [are available](https://www.zotero.org/styles). You also specify the location of your bibtex reference file in the YAML. You can call your reference file anything you like, I just used the generic word `references.bib` but giving it a more descriptive name is probably better.

# References

### 2021-09-17 products/manuscript/Manuscript.Rmd
.

@@
 ## General Background Information
-During the COVID-19 pandemic, the government of Bangladesh adopted nationwide lockdown.
-There has been some studies that showed its adverse  effect on people of Bangladesh.
-As the government has taken the vaccination program very strictly, it was expected to see a large number of population would get vaccinated.
-But as the reality was the opposite, we wanted to know why people are not getting vaccinated enough despite being affected by COVID-19 lockdown.
-Our research will shed somelight on Bangladeshi people's vaccine hesitancy.
+During the COVID-19 pandemic, the government of Bangladesh adopted nationwide lockdown.\ There has been some studies that showed its adverse  effect on people of Bangladesh.\ As the government has taken the vaccination program very strictly, it was expected to see a large number of population would get vaccinated.\ But as the reality was the opposite, we wanted to know why people are not getting vaccinated enough despite being affected by COVID-19 lockdown.\ Our research will shed somelight on Bangladeshi people's vaccine hesitancy.
 Als briefly, out work will present its relation to mental wellness.
@@
 ## Questions/Hypotheses to be addressed
-The main question is to find out why people gets hesitant to get vaccinated.
-Finding out their key motivator is the prime goal.
-Also, how mental wellness after covid-19 lockdown might affect their hesitant desition to get vaccinated, is another question we want to answer.
+The main question is to find out why people gets hesitant to get vaccinated.\ Finding out their key motivator is the prime goal.\ Also, how mental wellness after covid-19 lockdown might affect their hesitant desition to get vaccinated, is another question we want to answer.\
 

### 2021-10-01 products/manuscript/Manuscript.Rmd
updated

--- 2021-09-17 products/manuscript/Manuscript.Rmd
@@
 ---
-title: "Example Manuscript Template for a Data Analysis Project"
+title: "Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in nine low-and middle-income countries: an online survey"
 subtitle: ""
-author: Andreas Handel
+author: Ehsan Suez
 date: "`r Sys.Date()`"
@@
 ## General Background Information
-During the COVID-19 pandemic, the government of Bangladesh adopted nationwide lockdown.
-There has been some studies that showed its adverse  effect on people of Bangladesh.
-As the government has taken the vaccination program very strictly, it was expected to see a large number of population would get vaccinated.
-But as the reality was the opposite, we wanted to know why people are not getting vaccinated enough despite being affected by COVID-19 lockdown.
-Our research will shed somelight on Bangladeshi people's vaccine hesitancy.
-Als briefly, out work will present its relation to mental wellness.
+This study aimed to investigate, using the Andersen’s model of health care utilization, factors associated with COVID-19 testing among adults in Bangladesh.
 
 ## Description of data and data source
-Data was/will be collected using online questionnaire.
+This will be a descriptive cross-sectional online study.
+To get data for this study, between 10 December 2020 and 9 February 2021 an online survey was organized in Bangladesh.
+In total 759 adults (median age 45 years, interquartile range 33-57 years, range 18-93 years), participated in the study.
+COVID-19 testing/infection status was assessed by self-report.
 
 ## Questions/Hypotheses to be addressed
-The main question is to find out why people gets hesitant to get vaccinated.
-Finding out their key motivator is the prime goal.
-Also, how mental wellness after covid-19 lockdown might affect their hesitant desition to get vaccinated, is another question we want to answer.
-
-[I still haven't got access to the data. As soon as I get access to the data, I can update more information like how many subjects were included and info like that.]
+The main question is to find out the key factors associated with covid-19 testing
 
@@
 
-_In most research papers, results and methods are separate. You can combine them here if you find it easier. You are also welcome to structure things such that those are separate sections._
+_Study design, sample, and procedure_
+
+This will be a descriptive cross-sectional online study conducted in Bangladesh between 10 December 2020 to 9 February 2021.
+Participant inclusion criteria were 18 years and older, any gender, and provision of electronic informed consent.
+
+_Measures_
+Using Andersen’s model of health care utilization [Andersen 1995], study variables will be categorized into outcome variable, predisposing factors, enabling/disabling factors and need for care factors.
+
+_Outcome variable_
+COVID-19 testing/infection status will be assessed with the question, “Since the beginning of the COVID-19 outbreak, do you have information on your infection status?” Response options were 1=not tested/does not know test results, 2=negative, and 3=positive.
+
+_Predisposing factors_
+Sociodemographic factors included age, sex, country of residence, educational level, and the (estimated) age(s) of their housemate(s).
+Chronic/underlying diseases includs heart disease, hypertension, diabetes, cancer, HIV, tuberculosis, and chronic asthma; coded as “0” none and “1” at least presence of one clinically diagnosed condition.
+
+_COVID-19 preventive measures_
+Participants were asked, “During the past 7 days, have you been observing any of the following preventive measures against COVID-19?
+1) Social distancing of at least 1.5m, 2) Wearing a face mask, 3) Hand hygiene (regular handwashing with soap or using hand gel), and 4) Coughing hygiene (covering the mouth when coughing or sneezing).
+A composite non-adherence to all four COVID-19 preventive measure was calculated by coding each negative response with “1”, summing scores ranging from 0-4 (Cronbach’s alpha 0.7).
+
+_Enabling/disabling factors_
+Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel.
+
+_Disabling factors_ include the assessment of psychological distress with the Patient Health Questionnaire (PHQ-4) for Depression and Anxiety symptoms [Kroenke/ Löwe].
+The severity of psychological distress is categorized as normal (0-2), mild (3-5).
+moderate (6-8) and severe (9-12) based on the PHQ-4 scores.
+
+_Need for care factors_ include two questions on 1) the level of fear/worry of being infected with COVID-19 (ranging from 1=not at all worried to 5=extremely worried), and 2) having been quarantined (either at home or elsewhere) at any point in time during the COVID-19 epidemic.
+
+_Data analysis_
+
+Descriptive statistics will be used to describe the study population.
+Logistic regression will be used to assess associations between predisposing factors, enabling and disabling factors, need of care factors and COVID-19 testing status, COVID-19 positive versus negative status and COVID-19 positive versus negative and not tested status.
+Variables significant at <0.05 in univariate analyses were subsequently included in the multivariable logistic regression models.
+Statistical analyses will conducted using R.
 
@@
 
-```{r summarytable,  echo=FALSE}
-resulttable=readRDS("../../results/summarytable.rds")
-knitr::kable(resulttable, caption = 'Data summary table.')
-```
+#```{r summarytable,  echo=FALSE}
+#resulttable=readRDS("../../results/summarytable.rds")
+#knitr::kable(resulttable, caption = 'Data summary table.')
+#```
 
@@
 
-```{r resultfigure,  fig.cap='Analysis figure.', echo=FALSE}
-knitr::include_graphics("../../results/resultfigure.png")
-```
+#```{r resultfigure,  fig.cap='Analysis figure.', echo=FALSE}
+#knitr::include_graphics("../../results/resultfigure.png")
+#```
 
@@
 
-```{r resulttable,  echo=FALSE}
-resulttable=readRDS("../../results/resulttable.rds")
-knitr::kable(resulttable, caption = 'Linear model fit table.')
-```
+###```{r resulttable,  echo=FALSE}
+###resulttable=readRDS("../../results/resulttable.rds")
+###knitr::kable(resulttable, caption = 'Linear model fit table.')
+#```
 

### 2021-10-07 products/manuscript/Manuscript.Rmd
.

@@
 
-## Data import and cleaning
-_Write code that reads in the file and cleans it so it's ready for analysis.
-Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts.
-If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g.
-as supplement in a paper).
-All materials, including files that contain code, should be commented well so everyone can follow along._
+## Data import and cleaning_ [Here I mostly covered descriptive analysis]
+---
+title: "try"
+author: "Ehsan"
+date: "10/6/2021"
+output: html_document
+---
+```{r}
+library(ggplot2)
+library(tidyverse)
+library("readxl")
+```
+
+```{r}
+data1 <- readxl::read_excel('~/Study /MADA_2021/EhsanSuez-MADA-project/data/raw_data/Covid Vaccine data_Bangladesh_Abu_Sayeed.xlsx')
+```
+
+#I want to see how many NA values are there for each column. So, I wrote the following code. For manuscript we dont need it.
+#```{r}
+cbind(
+      lapply(
+             lapply(data1, is.na)
+             , sum)
+  )
+#
+#I want to see which columns have NA values
+```{r}
+df <- as.data.frame(
+      cbind(
+             lapply(
+                   lapply(data1, is.na), sum)
+        )
+   )
+rownames(subset(df, df$V1 != 0))
+```
+#the mean age and SD of mean age:
+```{r}
+mean(data1$Age)
+sd(data1$Age)
+```
+#For each age group, whats their percentage?
+```{r}
+data1 %>% 
+     group_by( Age ) %>% 
+     summarise( percent = 100 * n() / nrow( data1) )
+```
+#number of male and female
+```{r}
+sum(data1$Sex=='Male')
+sum(data1$Sex=='Female')
+```
+#percentage of male and female
+```{r}
+data1 %>% 
+     group_by( Sex ) %>% 
+     summarise( percent = 100 * n() / nrow( data1) )
+
+```
+#number of people for each educational category
+```{r}
+table(data1$`Highest educational level`)
+```
+```{r}
+sum(data1$'Highest educational level' == 'Primary')
+sum(data1$'Highest educational level' == 'Secondary')
+sum(data1$'Highest educational level' == 'University Postgraduate degree holder')
+sum(data1$'Highest educational level' == 'University Undergraduate degree holder')
+```
+#percentage of people for each student category
+```{r}
+data1 %>% 
+     group_by( `Highest educational level` ) %>% 
+     summarise( percent = 100 * n() / nrow( data1) )
+```
+#student/worker in the heathcare sector?
+```{r}
+table(data1$`Are you a student or worker in the healthcare sector?`)
+```
+#household members?
+```{r}
+table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 60 years and above`)
+table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 18 to 59 years`)
+table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: 12 to 17 years`)
+table(data1$`Who do you currently live with in the same household? Please select the number of persons in each age category.: Less than 12 years`)
+```
+```{r}
+table(data1$`Which of the following categories best describes your current socio-economic situation?`)
+```
+```{r}
+sum(data1$'Which of the following categories best describes your current socio-economic situation?' == 'High income category')
+sum(data1$'Which of the following categories best describes your current socio-economic situation?' == 'Low income category')
+sum(data1$'Which of the following categories best describes your current socio-economic situation?' == 'Lower middle income category')
+sum(data1$'Which of the following categories best describes your current socio-economic situation?' == 'Upper middle income category ')
+```
+
+#percentage of income category?
+```{r}
+data1 %>% 
+     group_by( `Which of the following categories best describes your current socio-economic situation?` ) %>% 
+     summarise( percent = 100 * n() / nrow( data1) )
+```
+```{r}
+table(data1$`Do you live in:`)
+```
+```{r}
+sum(data1$'Do you live in:' == 'A rural place / village')
+sum(data1$'Do you live in:' == 'A Sub-urban setting / urban slum')
+sum(data1$'Do you live in:' == 'An urban setting / city / town')
+```
+#percentage of living setup?
+```{r}
+data1 %>% 
+     group_by( `Do you live in:` ) %>% 
+     summarise( percent = 100 * n() / nrow( data1) )
+```
+```{r}
+table(data1$`Which source of COVID-19 information/advice do you trust the most?`)
+```
+
+```{r}
+sum(data1$'Are you currently working/studying from home because of the COVID-19 outbreak?' == 'No')
+sum(data1$'Are you currently working/studying from home because of the COVID-19 outbreak?' == 'Yes')
+```
+
+#percentage of work from home or not?
+```{r}
+data1 %>% 
+     group_by( `Are you currently working/studying from home because of the COVID-19 outbreak?` ) %>% 
+     summarise( percent = 100 * n() / nrow( data1) )
+```
+#Descriptive analysis for each question?
+```{r}
+table(data1$`Have you been quarantined (either at home or else where) at any point in time during the Covid-19 epidemic?`)
+```
+```{r}
+table(data1$`Since the beginning of the COVID-19 outbreak, do you have information on your infection status?`)
+```
+```{r}
+table(data1$`How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5`)
+```
+```{r}
+table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Heart disease`)
+```
+```{r}
+table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Hypertension`)
+```
+```{r}
+table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Diabetes`)
+```
+```{r}
+table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Cancer`)
+```
+```{r}
+table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): HIV`)
+```
+```{r}
+table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Tuberculosis`)
+```
+```{r}
+table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Asthma`)
+```
+```{r}
+table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above`)
+```
+```{r}
+table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Social distancing of at least 1.5m`)
+```
+```{r}
+table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Wearing face mask`)
+```
+```{r}
+table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19?
+(Tick all answers that apply): Hand hygiene (regular handwashing with soap or using hand gel)`)
+```
+```{r}
+table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19?
+(Tick all answers that apply): Coughing hygiene (covering mouth when coughing or sneezing)`)
+```
+```{r}
+table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): None of the above`)
+```
+```{r}
+table(data1$`During the past two weeks, how often have you been bothered by each of the following symptoms?: Feeling down, depressed, or hopeless (low spirits)`)
+```
+```{r}
+table(data1$`During the past two weeks, how often have you been bothered by each of the following symptoms?: Little interest or pleasure in doing things`)
+```
+```{r}
+table(data1$`During the past two weeks, how often have you been bothered by each of the following symptoms?: Not being able to stop or control worrying`)
+```
+```{r}
+table(data1$`During the past two weeks, how often have you been bothered by each of the following symptoms?: Feeling nervous, anxious or on edge`)
+```
+```{r}
+table(data1$`In your opinion, can someone be re-infected with coronavirus after recovering from a previous COVID-19 infection?`)
+```
+```{r}
+table(data1$`In your opinion, can COVID-19 infection be prevented by a vaccine?`)
+```
+```{r}
+table(data1$`To the best of your knowledge, is there currently an effective vaccine against COVID-19?`)
+```
+```{r}
+table(data1$`Would you be willing to take the COVID-19 vaccine when it becomes available?: If it is at least 50% effective`)
+```
+```{r}
+table(data1$`Would you be willing to take the COVID-19 vaccine when it becomes available?: If it is at least 75% effective`)
+```
+```{r}
+table(data1$`Would you be willing to take the COVID-19 vaccine when it becomes available?: If it is at least 90% effective`)
+```
+```{r}
+table(data1$`Would you be willing to allow your children take the COVID-19 vaccine when it becomes available?: If it is at least 95% effective`)
+```
+```{r}
+table(data1$`What are some of the possible reasons why you would hesitate to take the COVID-19 vaccine? (many answers possible):  I don't think COVID-19 existsists`)
+```
+```{r}
+table(data1$`What are some of the possible reasons why you would hesitate to take the COVID-19 vaccine? (many answers possible): I think the vaccine is not effective`)
+```
+```{r}
+table(data1$`What are some of the possible reasons why you would hesitate to take the COVID-19 vaccine? (many answers possible): I think the vaccine is designed to harm us`)
+```
+```{r}
+table(data1$`What are some of the possible reasons why you would hesitate to take the COVID-19 vaccine? (many answers possible): I am scared of side-effects of the vaccine`)
+```
+```{r}
+table(data1$`What are some of the possible reasons why you would hesitate to take the COVID-19 vaccine? (many answers possible): My body is naturally strong, I don't need a vaccine to fight COVID-19`)
+```
+```{r}
+table(data1$`What are some of the possible reasons why you would hesitate to take the COVID-19 vaccine? (many answers possible): I already had COVID-19, so I think I am immune to the disease`)
+```
+```{r}
+table(data1$`What are some of the possible reasons why you would hesitate to take the COVID-19 vaccine?
+(many answers possible): The COVID-19 pandemic is finished in my country, no need for a vaccine now`)
+```
+```{r}
+table(data1$`What are some of the possible reasons why you would hesitate to take the COVID-19 vaccine? (many answers possible): None of the above`)
+```
+```{r}
+table(data1$`What are some of the possible reasons why you would hesitate to take the COVID-19 vaccine? (many answers possible): Other reasons (please specify)`)
+```
+```{r}
+table(data1$`Please specify other reasons for hesitating to receive the COVID-19 vaccine:`)
+```
+```{r}
+table(data1$`How important is it to you that by getting the COVID-19 vaccine, you would protect your own health?: On a scale of 1 to 5`)
+```
+```{r}
+table(data1$`How important is it to you that by getting the COVID-19 vaccine, you would protect the health of other people in your community?: On a scale of 1 to 5`)
+```
+```{r}
+table(data1$`I fully understand what this study is about, and I freely consent to participate.
+All the information I provide can be used by researchers to better understand coronavirus disease in my country.`)
+```
 

### 2021-10-27 code/analysis_code/exploratory.Rmd
Part 2 updated.

--- 2021-10-07 products/manuscript/Manuscript.Rmd
@@
 ---
-title: "Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in nine low-and middle-income countries: an online survey"
-subtitle: ""
-author: Ehsan Suez
-date: "`r Sys.Date()`"
-site: bookdown::bookdown_site
-documentclass: article
-output:
-  bookdown::word_document2: 
-    toc: false
-    number_sections: true
-  bookdown::html_document2: 
-    toc: false
-bibliography: ../references.bib
-csl: ../apa.csl
+title: "exploratory"
+author: "Ehsan"
+date: "10/27/2021"
+output: html_document
 ---
 
-The structure below is a possible setup for a data analysis project (including the course project). For a manuscript, adjust as needed.
-
-# Summary/Abstract
-_Write a summary of your project._
-
-# Introduction
-
-## General Background Information
-This study aimed to investigate, using the Andersen’s model of health care utilization, factors associated with COVID-19 testing among adults in Bangladesh.
-
-## Description of data and data source
-This will be a descriptive cross-sectional online study.
-To get data for this study, between 10 December 2020 and 9 February 2021 an online survey was organized in Bangladesh.
-In total 759 adults (median age 45 years, interquartile range 33-57 years, range 18-93 years), participated in the study.
-COVID-19 testing/infection status was assessed by self-report.
-
-## Questions/Hypotheses to be addressed
-The main question is to find out the key factors associated with covid-19 testing
-
-# Methods and Results
-
-_Study design, sample, and procedure_
-
-This will be a descriptive cross-sectional online study conducted in Bangladesh between 10 December 2020 to 9 February 2021.
-Participant inclusion criteria were 18 years and older, any gender, and provision of electronic informed consent.
-
-_Measures_
-Using Andersen’s model of health care utilization [Andersen 1995], study variables will be categorized into outcome variable, predisposing factors, enabling/disabling factors and need for care factors.
-
-_Outcome variable_
-COVID-19 testing/infection status will be assessed with the question, “Since the beginning of the COVID-19 outbreak, do you have information on your infection status?” Response options were 1=not tested/does not know test results, 2=negative, and 3=positive.
-
-_Predisposing factors_
-Sociodemographic factors included age, sex, country of residence, educational level, and the (estimated) age(s) of their housemate(s).
-Chronic/underlying diseases includs heart disease, hypertension, diabetes, cancer, HIV, tuberculosis, and chronic asthma; coded as “0” none and “1” at least presence of one clinically diagnosed condition.
-
-_COVID-19 preventive measures_
-Participants were asked, “During the past 7 days, have you been observing any of the following preventive measures against COVID-19?
-1) Social distancing of at least 1.5m, 2) Wearing a face mask, 3) Hand hygiene (regular handwashing with soap or using hand gel), and 4) Coughing hygiene (covering the mouth when coughing or sneezing).
-A composite non-adherence to all four COVID-19 preventive measure was calculated by coding each negative response with “1”, summing scores ranging from 0-4 (Cronbach’s alpha 0.7).
-
-_Enabling/disabling factors_
-Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel.
-
-_Disabling factors_ include the assessment of psychological distress with the Patient Health Questionnaire (PHQ-4) for Depression and Anxiety symptoms [Kroenke/ Löwe].
-The severity of psychological distress is categorized as normal (0-2), mild (3-5).
-moderate (6-8) and severe (9-12) based on the PHQ-4 scores.
-
-_Need for care factors_ include two questions on 1) the level of fear/worry of being infected with COVID-19 (ranging from 1=not at all worried to 5=extremely worried), and 2) having been quarantined (either at home or elsewhere) at any point in time during the COVID-19 epidemic.
-
-_Data analysis_
-
-Descriptive statistics will be used to describe the study population.
-Logistic regression will be used to assess associations between predisposing factors, enabling and disabling factors, need of care factors and COVID-19 testing status, COVID-19 positive versus negative status and COVID-19 positive versus negative and not tested status.
-Variables significant at <0.05 in univariate analyses were subsequently included in the multivariable logistic regression models.
-Statistical analyses will conducted using R.
-
-## Data aquisition
-_As applicable, explain where and how you got the data. If you directly import the data from an online source, you can combine this section with the next._
-
-## Data import and cleaning_ [Here I mostly covered descriptive analysis]
----
-title: "try"
-author: "Ehsan"
-date: "10/6/2021"
-output: html_document
----
 ```{r}
@@
 library("readxl")
+library(here)
 ```
 
+#Read data
 ```{r}
-data1 <- readxl::read_excel('~/Study /MADA_2021/EhsanSuez-MADA-project/data/raw_data/Covid Vaccine data_Bangladesh_Abu_Sayeed.xlsx')
+data_location <- here::here("data","processed_data","processeddata.rds")
+data1 <- readRDS(data_location)
 ```
@@
 #I want to see how many NA values are there for each column. So, I wrote the following code. For manuscript we dont need it.
-#```{r}
+```{r}
 cbind(
@@
   )
+```
 #
@@
      summarise( percent = 100 * n() / nrow( data1) )
-
 ```
@@
 ```
-
-## Exploratory analysis
-
-_Use a combination of text/tables/figures to explore and describe your data.
-You should produce plots or tables or other summary quantities for the most interesting/important quantities in your data.
-Depending on the total number of variables in your dataset, explore all or some of the others.
-FIgures produced here might be histograms or density plots, correlation plots, etc.
-Tables might summarize your data._
-
-_Continue by creating plots or tables of the outcome(s) of interest and the predictor/exposure/input variables you are most interested in.
-If your dataset is small, you can do that for all variables.
-Plots produced here can be scatterplots, boxplots, violinplots, etc.
-Tables can be simple 2x2 tables or larger ones._
-
-_To get some further insight into your data, if reasonable you could compute simple statistics (e.g.
-t-tests, simple regression model with 1 predictor, etc.) to look for associations between your outcome(s) and each individual predictor variable.
-Though note that unless you pre-specified the outcome and main exposure, any "p<0.05 means statistical significance" interpretation is not valid._
-
-Table \@ref(tab:summarytable) shows a table summarizing the data.
-
-#```{r summarytable,  echo=FALSE}
-#resulttable=readRDS("../../results/summarytable.rds")
-#knitr::kable(resulttable, caption = 'Data summary table.')
-#```
-
-Figure \@ref(fig:resultfigure) shows a scatterplot figure produced by one of the R scripts.
-
-#```{r resultfigure,  fig.cap='Analysis figure.', echo=FALSE}
-#knitr::include_graphics("../../results/resultfigure.png")
-#```
-
-## Full analysis
-
-_Use one or several suitable statistical/machine learning methods to analyze your data and to produce meaningful figures, tables, etc.
-This might again be code that is best placed in one or several separate R scripts that need to be well documented.
-You want the code to produce figures and data ready for display as tables, and save those.
-Then you load them here._
-
-Example table \@ref(tab:resulttable) shows a table summarizing a linear model fit.
-
-###```{r resulttable,  echo=FALSE}
-###resulttable=readRDS("../../results/resulttable.rds")
-###knitr::kable(resulttable, caption = 'Linear model fit table.')
-#```
-
-# Discussion
-
-## Summary and Interpretation
-_Summarize what you did, what you found and what it means._
-
-## Strengths and Limitations
-_Discuss what you perceive as strengths and limitations of your analysis._
-
-## Conclusions
-_What are the main take-home messages?_
-
-_Include citations in your Rmd file using bibtex, the list of references will automatically be placed at the end_
-
-This paper [@Leek2015a] discusses types of analyses.
-
-Note that this cited reference will show up at the end of the document, the reference formatting is determined by the CSL file specified in the YAML header.
-Many more style files for almost any journal [are available](https://www.zotero.org/styles).
-You also specify the location of your bibtex reference file in the YAML.
-You can call your reference file anything you like, I just used the generic word `references.bib` but giving it a more descriptive name is probably better.
-
-# References

### 2021-10-27 products/manuscript/Manuscript.Rmd
Part 2 updated.

--- 2021-10-01 products/manuscript/Manuscript.Rmd
@@
 
-## Data import and cleaning
-_Write code that reads in the file and cleans it so it's ready for analysis.
-Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts.
-If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g.
-as supplement in a paper).
-All materials, including files that contain code, should be commented well so everyone can follow along._
+## Data import and cleaning_ [Here I mostly covered descriptive analysis]
+---
+title: "try"
+author: "Ehsan"
+date: "10/6/2021"
+output: html_document
+---
 
@@
 Table \@ref(tab:summarytable) shows a table summarizing the data.
-
-#```{r summarytable,  echo=FALSE}
-#resulttable=readRDS("../../results/summarytable.rds")
-#knitr::kable(resulttable, caption = 'Data summary table.')
-#```
-
-Figure \@ref(fig:resultfigure) shows a scatterplot figure produced by one of the R scripts.
-
-#```{r resultfigure,  fig.cap='Analysis figure.', echo=FALSE}
-#knitr::include_graphics("../../results/resultfigure.png")
-#```
-
-## Full analysis
-
-_Use one or several suitable statistical/machine learning methods to analyze your data and to produce meaningful figures, tables, etc.
-This might again be code that is best placed in one or several separate R scripts that need to be well documented.
-You want the code to produce figures and data ready for display as tables, and save those.
-Then you load them here._
-
-Example table \@ref(tab:resulttable) shows a table summarizing a linear model fit.
-
-###```{r resulttable,  echo=FALSE}
-###resulttable=readRDS("../../results/resulttable.rds")
-###knitr::kable(resulttable, caption = 'Linear model fit table.')
-#```
 

### 2021-10-27 code/processing_code/processingscript.R

@@ -11,45 +11,17 @@ library(here) #to set paths
 
 #path to data
 #note the use of the here() package and not absolute paths
-data_location <- here::here("data","raw_data","exampledata.xlsx")
+data_location <- here::here("data","raw_data","Covid Vaccine data_Bangladesh_Abu_Sayeed.xlsx")
+ 
 
-#load data. 
-#note that for functions that come from specific packages (instead of base R)
-# I often specify both package and function like so
-#package::function() that's not required one could just call the function
-#specifying the package makes it clearer where the function "lives",
 #but it adds typing. You can do it either way.
 rawdata <- readxl::read_excel(data_location)
 
-#take a look at the data
-dplyr::glimpse(rawdata)
 
-#dataset is so small, we can print it to the screen.
-#that is often not possible.
-print(rawdata)
+processeddata <- rawdata
+                     
 
-# looks like we have measurements for height (in centimeters) and weight (in kilogram)
 
-# there are some problems with the data: 
-# There is an entry which says "sixty" instead of a number. 
-# Does that mean it should be a numeric 60? It somehow doesn't make
-# sense since the weight is 60kg, which can't happen for a 60cm person (a baby)
-# Since we don't know how to fix this, we need to remove the person.
-# This "sixty" entry also turned all Height entries into characters instead of numeric.
-# We need to fix that too.
-# Then there is one person with a height of 6. 
-# that could be a typo, or someone mistakenly entered their height in feet.
-# Since we unfortunately don't know, we'll have to remove this person.
-# similarly, there is a person with weight of 7000, which is impossible,
-# and one person with missing weight.
-# to be able to analyze the data, we'll remove those 5 individuals
-
-# this is one way of doing it. Note that if the data gets updated, 
-# we need to decide if the thresholds are ok (newborns could be <50)
-
-processeddata <- rawdata %>% dplyr::filter( Height != "sixty" ) %>% 
-                             dplyr::mutate(Height = as.numeric(Height)) %>% 
-                             dplyr::filter(Height > 50 & Weight < 1000)
 
 # save data as RDS
 # I suggest you save your processed and cleaned data as RDS or RDA/Rdata files. 

### 2021-10-27 code/analysis_code/exploratory.Rmd
more exploratory

@@
 data1 %>% 
-     group_by( Age ) %>% 
+     group_by(Age) %>%
      summarise( percent = 100 * n() / nrow( data1) )
+
 ```
-#number of male and female
+#people over 40
 ```{r}
-sum(data1$Sex=='Male')
-sum(data1$Sex=='Female')
+data1 %>% 
+     dplyr::filter(Age > 40 ) %>%
+     group_by(Age) %>%
+     summarise( percent = 100 * n() / nrow( data1) )
+
 ```
+
 #percentage of male and female
@@
 ```
+#percentage of student/health worker
+
+```{r}
+data1 %>% 
+     group_by( `Are you a student or worker in the healthcare sector?` ) %>% 
+     summarise( percent = 100 * n() / nrow( data1) )
+```
+
 #household members?
@@
 ```
+#most trusted source?
+```{r}
+data1 %>% 
+     group_by( `Which source of COVID-19 information/advice do you trust the most?` ) %>% 
+     summarise( percent = 100 * n() / nrow( data1) )
+```
 
@@
 ```
+#correct knowledge of their status
+```{r}
+data1 %>% 
+     group_by( `Since the beginning of the COVID-19 outbreak, do you have information on your infection status?` ) %>% 
+     summarise( percent = 100 * n() / nrow( data1) )
+```
+
 ```{r}
@@
 ```
+#worried about re-infection
+```{r}
+data1 %>% 
+     group_by( `How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5` ) %>% 
+     summarise( percent = 100 * n() / nrow( data1) )
+```
+
 ```{r}
@@
 ```{r}
+data1 %>% 
+     group_by( `Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above` ) %>% 
+     summarise( percent = 100 * n() / nrow( data1) )
+```
+
+```{r}
 table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Social distancing of at least 1.5m`)
@@
 ```
+```{r}
+data1 %>% 
+     group_by( `During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): None of the above` ) %>% 
+     summarise( percent = 100 * n() / nrow( data1) )
+```
+
 ```{r}

### 2021-10-27 code/analysis_code/exploratory.Rmd
more processing

@@
 library("readxl")
+library(dplyr)
 library(here)
@@
 ```{r}
-table(data1$`Highest educational level`)
+table(data1$`education`)
 ```
 ```{r}
-sum(data1$'Highest educational level' == 'Primary')
-sum(data1$'Highest educational level' == 'Secondary')
-sum(data1$'Highest educational level' == 'University Postgraduate degree holder')
-sum(data1$'Highest educational level' == 'University Undergraduate degree holder')
+sum(data1$'education' == 'Primary')
+sum(data1$'education' == 'Secondary')
+sum(data1$'education' == 'University Postgraduate degree holder')
+sum(data1$'education' == 'University Undergraduate degree holder')
 ```
@@
 data1 %>% 
-     group_by( `Highest educational level` ) %>% 
+     group_by( `education` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
@@
 ```{r}
-table(data1$`Are you a student or worker in the healthcare sector?`)
+table(data1$`student/heathworker`)
 ```
+
 #percentage of student/health worker
@@
 data1 %>% 
-     group_by( `Are you a student or worker in the healthcare sector?` ) %>% 
+     group_by( `student/heathworker` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
@@
 ```{r}
-table(data1$`Which of the following categories best describes your current socio-economic situation?`)
+table(data1$`economic_status`)
 ```
 ```{r}
-sum(data1$'Which of the following categories best describes your current socio-economic situation?' == 'High income category')
-sum(data1$'Which of the following categories best describes your current socio-economic situation?' == 'Low income category')
-sum(data1$'Which of the following categories best describes your current socio-economic situation?' == 'Lower middle income category')
-sum(data1$'Which of the following categories best describes your current socio-economic situation?' == 'Upper middle income category ')
+sum(data1$'economic_status' == 'High income category')
+sum(data1$'economic_status' == 'Low income category')
+sum(data1$'economic_status' == 'Lower middle income category')
+sum(data1$'economic_status' == 'Upper middle income category ')
 ```
@@
 data1 %>% 
-     group_by( `Which of the following categories best describes your current socio-economic situation?` ) %>% 
+     group_by( `economic_status` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
@@
 ```{r}
-table(data1$`Do you live in:`)
+table(data1$`residence`)
 ```
 ```{r}
-sum(data1$'Do you live in:' == 'A rural place / village')
-sum(data1$'Do you live in:' == 'A Sub-urban setting / urban slum')
-sum(data1$'Do you live in:' == 'An urban setting / city / town')
+sum(data1$'residence' == 'A rural place / village')
+sum(data1$'residence' == 'A Sub-urban setting / urban slum')
+sum(data1$'residence' == 'An urban setting / city / town')
 ```
@@
 data1 %>% 
-     group_by( `Do you live in:` ) %>% 
+     group_by( `residence` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
 ```
+
 ```{r}
-table(data1$`Which source of COVID-19 information/advice do you trust the most?`)
+table(data1$`trusted_source`)
 ```
@@
 data1 %>% 
-     group_by( `Which source of COVID-19 information/advice do you trust the most?` ) %>% 
+     group_by( `trusted_source` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
@@
 ```{r}
-sum(data1$'Are you currently working/studying from home because of the COVID-19 outbreak?' == 'No')
-sum(data1$'Are you currently working/studying from home because of the COVID-19 outbreak?' == 'Yes')
+sum(data1$'work_from_home' == 'No')
+sum(data1$'work_from_home' == 'Yes')
 ```
@@
 data1 %>% 
-     group_by( `Are you currently working/studying from home because of the COVID-19 outbreak?` ) %>% 
+     group_by( `work_from_home` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
@@
 ```{r}
-table(data1$`Have you been quarantined (either at home or else where) at any point in time during the Covid-19 epidemic?`)
+table(data1$`quarantined_or_not`)
 ```
+#Quarantined or not
 ```{r}
-table(data1$`Since the beginning of the COVID-19 outbreak, do you have information on your infection status?`)
+data1 %>% 
+     group_by( `quarantined_or_not` ) %>% 
+     summarise( percent = 100 * n() / nrow( data1) )
+```
+
+```{r}
+table(data1$`infection_status_info`)
 ```
@@
 data1 %>% 
-     group_by( `Since the beginning of the COVID-19 outbreak, do you have information on your infection status?` ) %>% 
+     group_by( `infection_status_info` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
@@
 ```{r}
-table(data1$`How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5`)
+table(data1$`worry_level`)
 ```
@@
 data1 %>% 
-     group_by( `How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5` ) %>% 
+     group_by( `worry_level` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )

### 2021-10-27 code/processing_code/processingscript.Rmd
more processing

---
title: "preprocessing"
author: "Ehsan"
date: "10/27/2021"
output: html_document
---

# processing script
#
#this script loads the raw data, processes and cleans it 
#and saves it as Rds file in the processed_data folder

#load needed packages. make sure they are installed.
```{r}
library(readxl) #for loading Excel files
library(dplyr) #for data processing
library(here) #to set paths
```

#path to data
#note the use of the here() package and not absolute paths
```{r}
data_location <- here::here("data","raw_data","Covid Vaccine data_Bangladesh_Abu_Sayeed.xlsx")
```

#but it adds typing. You can do it either way.
```{r}
rawdata <- readxl::read_excel(data_location)
```

```{r}
processeddata <- rawdata %>% rename ("education" = `Highest educational level`,
                               "student/heathworker" = `Are you a student or worker in the healthcare sector?`,
                               "economic_status" = 'Which of the following categories best describes your current socio-economic situation?',
                               "residence" = `Do you live in:`,
                               "trusted_source" = `Which source of COVID-19 information/advice do you trust the most?`,
                               "work_from_home" = 'Are you currently working/studying from home because of the COVID-19 outbreak?',
                               "quarantined_or_not" = `Have you been quarantined (either at home or else where) at any point in time during the Covid-19 epidemic?`,
                               "infection_status_info" = `Since the beginning of the COVID-19 outbreak, do you have information on your infection status?`,
                               "worry_level" = `How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5`,)
```

# save data as RDS
# I suggest you save your processed and cleaned data as RDS or RDA/Rdata files. 
# This preserves coding like factors, characters, numeric, etc. 
# If you save as CSV, that information would get lost.
# See here for some suggestions on how to store your processed data:
# http://www.sthda.com/english/wiki/saving-data-into-r-data-format-rds-and-rdata

# location to save file
```{r}
save_data_location <- here::here("data","processed_data","processeddata.rds")
```

```{r}
saveRDS(processeddata, file = save_data_location)
```

### 2021-10-27 code/processing_code/processingscript.R

@@ -1,38 +1,0 @@
-###############################
-# processing script
-#
-#this script loads the raw data, processes and cleans it 
-#and saves it as Rds file in the processed_data folder
-
-#load needed packages. make sure they are installed.
-library(readxl) #for loading Excel files
-library(dplyr) #for data processing
-library(here) #to set paths
-
-#path to data
-#note the use of the here() package and not absolute paths
-data_location <- here::here("data","raw_data","Covid Vaccine data_Bangladesh_Abu_Sayeed.xlsx")
- 
-
-#but it adds typing. You can do it either way.
-rawdata <- readxl::read_excel(data_location)
-
-
-processeddata <- rawdata
-                     
-
-
-
-# save data as RDS
-# I suggest you save your processed and cleaned data as RDS or RDA/Rdata files. 
-# This preserves coding like factors, characters, numeric, etc. 
-# If you save as CSV, that information would get lost.
-# See here for some suggestions on how to store your processed data:
-# http://www.sthda.com/english/wiki/saving-data-into-r-data-format-rds-and-rdata
-
-# location to save file
-save_data_location <- here::here("data","processed_data","processeddata.rds")
-
-saveRDS(processeddata, file = save_data_location)
-
-

### 2021-10-28 code/analysis_code/analysisscript.Rmd
more exploratory analysis + manuscript update

---
title: "analysis"
author: "Ehsan"
date: "10/27/2021"
output: html_document
---

```{r}
library(tidymodels)
library(readr)       # for importing data
library(tidyverse)
library(dotwhisker)
library(broom.mixed)
library(here)
```

### 2021-10-28 code/analysis_code/exploratory.Rmd
more exploratory analysis + manuscript update

@@
 data1 <- readRDS(data_location)
+```
+
+#check if certain column is factor or not
+```{r}
+is.factor(data1$Sex)
 ```
@@
 ```
-#people over 40
+#people below 35
 ```{r}
-data1 %>% 
-     dplyr::filter(Age > 40 ) %>%
+age_summary = data1 %>% 
+     dplyr::filter(Age < 36 ) %>%
      group_by(Age) %>%
      summarise( percent = 100 * n() / nrow( data1) )
-
+print(age_summary)
 ```
 
+```{r}
+df1 = data.frame(age_summary)
+summarytable_file = here("results", "summarytable.rds")
+saveRDS(df1, file = summarytable_file)
+```
 #percentage of male and female
 ```{r}
-data1 %>% 
+sex_summary =data1 %>% 
      group_by( Sex ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
+print(sex_summary)
 ```
+```{r}
+df2 = data.frame(sex_summary)
+summarytable_file = here("results", "summarytable2.rds")
+saveRDS(df2, file = summarytable_file)
+```
+
 #number of people for each educational category
@@
 ```{r}
-data1 %>% 
+education_summary = data1 %>% 
      group_by( `education` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
+print(education_summary)
 ```
+
+```{r}
+df3 = data.frame(education_summary)
+summarytable_file = here("results", "summarytable3.rds")
+saveRDS(df3, file = summarytable_file)
+```
+
 #student/worker in the heathcare sector?
@@
 ```{r}
-data1 %>% 
+income_summary = data1 %>% 
      group_by( `economic_status` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
+print(income_summary)
 ```
+```{r}
+df4 = data.frame(income_summary)
+summarytable_file = here("results", "summarytable4.rds")
+saveRDS(df4, file = summarytable_file)
+```
+
 ```{r}
@@
 ```{r}
-data1 %>% 
+residence_summary = data1 %>% 
      group_by( `residence` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
+print(residence_summary)
+```
+```{r}
+df5 = data.frame(residence_summary)
+summarytable_file = here("results", "summarytable5.rds")
+saveRDS(df5, file = summarytable_file)
 ```
@@
 ```{r}
-data1 %>% 
+source_summary = data1 %>% 
      group_by( `trusted_source` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
+print(source_summary)
+```
+```{r}
+df6 = data.frame(source_summary)
+summarytable_file = here("results", "summarytable6.rds")
+saveRDS(df6, file = summarytable_file)
 ```
@@
 ```{r}
-data1 %>% 
+work_From_home_or_not_Summary = data1 %>% 
      group_by( `work_from_home` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
+print(work_From_home_or_not_Summary)
 ```
+```{r}
+df7 = data.frame(work_From_home_or_not_Summary)
+summarytable_file = here("results", "summarytable7.rds")
+saveRDS(df7, file = summarytable_file)
+```
+
 #Descriptive analysis for each question?
@@
 ```{r}
-data1 %>% 
+q_or_not_summary = data1 %>% 
      group_by( `quarantined_or_not` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
+print(q_or_not_summary)
+```
+```{r}
+df8 = data.frame(q_or_not_summary)
+summarytable_file = here("results", "summarytable8.rds")
+saveRDS(df8, file = summarytable_file)
 ```
@@
 ```{r}
-data1 %>% 
+test_status_summary = data1 %>% 
      group_by( `infection_status_info` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
+print(test_status_summary)
+```
+```{r}
+df9 = data.frame(test_status_summary)
+summarytable_file = here("results", "summarytable9.rds")
+saveRDS(df9, file = summarytable_file)
+```
+#worried about re-infection
+```{r}
+worry_level_summary = data1 %>% 
+     group_by( `worry_level` ) %>% 
+     summarise( percent = 100 * n() / nrow( data1) )
+print(worry_level_summary)
+```
+```{r}
+df10 = data.frame(worry_level_summary)
+summarytable_file = here("results", "summarytable10.rds")
+saveRDS(df10, file = summarytable_file)
 ```
@@
 table(data1$`worry_level`)
-```
-#worried about re-infection
-```{r}
-data1 %>% 
-     group_by( `worry_level` ) %>% 
-     summarise( percent = 100 * n() / nrow( data1) )
 ```
@@
 ```{r}
-data1 %>% 
+chronic_disease_history = data1 %>% 
      group_by( `Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
+print(chronic_disease_history)
+```
+
+```{r}
+df11 = data.frame(chronic_disease_history)
+summarytable_file = here("results", "summarytable11.rds")
+saveRDS(df11, file = summarytable_file)
 ```

### 2021-10-28 products/manuscript/Manuscript.Rmd
more exploratory analysis + manuscript update

@@
 ---
-title: "Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in nine low-and middle-income countries: an online survey"
+title: "Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in Bangladesh: an online survey"
 subtitle: ""
@@
 
-_Enabling/disabling factors_
+_Enabling/d_
 Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel.
-
-_Disabling factors_ include the assessment of psychological distress with the Patient Health Questionnaire (PHQ-4) for Depression and Anxiety symptoms [Kroenke/ Löwe].
-The severity of psychological distress is categorized as normal (0-2), mild (3-5).
-moderate (6-8) and severe (9-12) based on the PHQ-4 scores.
 
@@
 
-## Data import and cleaning_ [Here I mostly covered descriptive analysis]
+## Data import and cleaning_ html_document
 ---
-title: "try"
-author: "Ehsan"
-date: "10/6/2021"
-output: html_document
----
-
+```{r}
+library(here)
+```
 ## Exploratory analysis
@@
 Tables might summarize your data._
+
+```{r summarytable,  echo=FALSE}
+resulttable=readRDS("../../results/summarytable.rds")
+knitr::kable(resulttable, caption = 'Age Percentage of Participants.')
+```
+78.9% of total participants are less than or equal  to 35 years old.
+
+```{r summarytable2,  echo=FALSE}
+resulttable=readRDS("../../results/summarytable2.rds")
+knitr::kable(resulttable, caption = 'Sex Percentage of Participants.')
+```
+
+```{r summarytable3,  echo=FALSE}
+resulttable=readRDS("../../results/summarytable3.rds")
+knitr::kable(resulttable, caption = 'Education Background Percentage of Participants.')
+```
+
+```{r summarytable4,  echo=FALSE}
+resulttable=readRDS("../../results/summarytable4.rds")
+knitr::kable(resulttable, caption = 'Income Percentage of Participants.')
+```
+
+```{r summarytable5,  echo=FALSE}
+resulttable=readRDS("../../results/summarytable5.rds")
+knitr::kable(resulttable, caption = 'Residence Percentage of Participants.')
+```
+
+```{r summarytable6,  echo=FALSE}
+resulttable=readRDS("../../results/summarytable6.rds")
+knitr::kable(resulttable, caption = 'Source of information Percentage of Participants.')
+```
+
+```{r summarytable7,  echo=FALSE}
+resulttable=readRDS("../../results/summarytable7.rds")
+knitr::kable(resulttable, caption = 'Percentage of Participants working from home or not.')
+```
+
+```{r summarytable8,  echo=FALSE}
+resulttable=readRDS("../../results/summarytable8.rds")
+knitr::kable(resulttable, caption = 'Percentage of Participants quarantined or not at some stage.')
+```
+
+```{r summarytable9,  echo=FALSE}
+resulttable=readRDS("../../results/summarytable9.rds")
+knitr::kable(resulttable, caption = 'Percentage of covid test status of the participants.')
+```
+
+```{r summarytable10,  echo=FALSE}
+resulttable=readRDS("../../results/summarytable10.rds")
+knitr::kable(resulttable, caption = "Percentage of participants' worry level about (re)infection with COVID-19.")
+```
+
+```{r summarytable11,  echo=FALSE}
+resulttable=readRDS("../../results/summarytable11.rds")
+knitr::kable(resulttable, caption = "Percentage of participants' history of chronic disease")
+```
 
@@
 Though note that unless you pre-specified the outcome and main exposure, any "p<0.05 means statistical significance" interpretation is not valid._
-
-Table \@ref(tab:summarytable) shows a table summarizing the data.
 

### 2021-10-28 code/processing_code/processingscript.Rmd
more exploratory analysis + manuscript update
.

@@
 library(here) #to set paths
+library(tidyverse)
 ```
@@
 
-# save data as RDS
-# I suggest you save your processed and cleaned data as RDS or RDA/Rdata files. 
-# This preserves coding like factors, characters, numeric, etc. 
-# If you save as CSV, that information would get lost.
-# See here for some suggestions on how to store your processed data:
-# http://www.sthda.com/english/wiki/saving-data-into-r-data-format-rds-and-rdata
-
 # location to save file
@@
 ```
+
+```{r}
+processeddata2 <- processeddata %>%
+                  mutate (infection_status_info = factor(infection_status_info)) 
+```
+
+```{r}
+str(processeddata2)
+```
+
+```{r}
+save_data_location <- here::here("data","processed_data","processeddata2.rds")
+```
+
+```{r}
+saveRDS(processeddata, file = save_data_location)
+```

### 2021-10-28 products/manuscript/Manuscript.Rmd
.

@@
 ```
-78.9% of total participants are less than or equal  to 35 years old.
+**78.9% of total participants are less than or equal  to 35 years old.**
 
@@
 ```
+**While 45.18% of the participants were female, 54.82% were male.**
 
@@
 ```
-
+**78.05% of the participants had a bachelor or post-bachelor degree**
 ```{r summarytable4,  echo=FALSE}
@@
 ```
-
+**Almost 50% of the participants belongs to "upper middle income category"**
 ```{r summarytable5,  echo=FALSE}
@@
 ```
-
+**Less than 10% of the participants live in a village/rural area**
 ```{r summarytable6,  echo=FALSE}
@@
 ```
-
+**Health professionals and Tv/radio seems to be the most trusted source to the participants.**
 ```{r summarytable7,  echo=FALSE}
@@
 ```
-
+**Apparently equal half of the participants worked from or not**
 ```{r summarytable8,  echo=FALSE}
@@
 ```
-
+**Major half of the participants did quarantine at some stage during the study**
 ```{r summarytable9,  echo=FALSE}
@@
 ```
-
+**63% of the participants didn't go through a COVID test**
 ```{r summarytable10,  echo=FALSE}
@@
 ```
-
+**Almost half of the participants (46%) were moderate or more worried about reinfection**
 ```{r summarytable11,  echo=FALSE}
@@
 ```
-
+**Only 22% of the participants recorded to have some sort of chronic disease**
 _Continue by creating plots or tables of the outcome(s) of interest and the predictor/exposure/input variables you are most interested in.

### 2021-11-03 code/analysis_code/analysisscript.Rmd
.
Part 3 continued. Reorganized the whole "Project" folder".

@@
 ```
+
+```{r}
+data_location <- here::here("data","processed_data","processeddata.rds")
+```
+
+#load data. 
+```{r}
+mydata <- readRDS(data_location)
+glimpse(mydata)
+```
+
+#The main "outcome variable" is the knowledge of infection status (positive/negative/not tested).
+There are "predisposing factors" (age, sex, education level, chronic disease history etc), "enabling factors" (socio-economic status, area of residence, source of covid news etc) and "need for care factors" (level of fear of reinfection, quarantined or not).
+We'll do logistic regression analysis for key factors of epredisposing, enabling and need for care factors.
+
+#We'll start with logistic regression model betweem infection status and Age, Sex, Education level (Key Predisposing Factors)
+```{r}
+lg_mod <- 
+       logistic_reg() %>% 
+       set_engine("glm")
+lg_fit <-
+       lg_mod %>%
+       fit(infection_status_info ~ Age + Sex + education, data = mydata)
+lg_fit
+```
+
+```{r}
+tidy(lg_fit)
+```
+
+```{r}
+lg_fit_table_predisposing <- tidy(lg_fit)
+```
+
+# saved it as a file
+```{r}
+summarytable_file12 = here("results", "lg_fit_table_predisposing.rds")
+saveRDS(lg_fit_table_predisposing, file = summarytable_file12)
+```
+
+```{r}
+glance(lg_fit)
+```
+
+```{r}
+lg_fit_statistics_predisposing <- glance(lg_fit)
+```
+
+# saved it as a file
+```{r}
+summarytable_file13 = here("results", "lg_fit_statistics_predisposing.rds")
+saveRDS(lg_fit_statistics_predisposing, file = summarytable_file13)
+```
+
+#Then, we'll do log model betweem infection status and socio economic status, area of residence,student/healthworker, source of covid news (Key enabling Factors)
+```{r}
+lg_fit1 <-
+       lg_mod %>%
+       fit(infection_status_info ~ economic_status + residence + trusted_source , data = mydata)
+lg_fit1
+```
+
+```{r}
+tidy(lg_fit1)
+```
+
+```{r}
+lg_fit_table_enabling <- tidy(lg_fit1)
+```
+
+# saved it as a file
+```{r}
+summarytable_file14 = here("results", "lg_fit_table_enabling.rds")
+saveRDS(lg_fit_table_enabling, file = summarytable_file14)
+```
+
+```{r}
+glance(lg_fit1)
+```
+
+```{r}
+lg_fit_statistics_enabling <- glance(lg_fit1)
+```
+
+# saved it as a file
+```{r}
+summarytable_file15 = here("results", "lg_fit_statistics_enabling.rds")
+saveRDS(lg_fit_statistics_enabling, file = summarytable_file15)
+```
+
+#Then, we'll do log model betweem infection status and level of fear of infection and quarantined or not (Key need for care factors )
+```{r}
+lg_fit2 <-
+       lg_mod %>%
+       fit(infection_status_info ~ quarantined_or_not + worry_level , data = mydata)
+lg_fit2
+```
+
+```{r}
+tidy(lg_fit2)
+```
+
+```{r}
+lg_fit_table_needforcare <- tidy(lg_fit2)
+```
+
+# saved it as a file
+```{r}
+summarytable_file16 = here("results", "lg_fit_table_needforcare.rds")
+saveRDS(lg_fit_table_needforcare, file = summarytable_file16)
+```
+
+```{r}
+glance(lg_fit2)
+```
+
+```{r}
+lg_fit_statistics_needforcare <- glance(lg_fit2)
+```
+
+# saved it as a file
+```{r}
+summarytable_file17 = here("results", "lg_fit_statistics_needforcare.rds")
+saveRDS(lg_fit_statistics_needforcare, file = summarytable_file17)
+```
+
+#compare three models
+```{r}
+compare_log_model <- anova(lg_fit$fit, lg_fit1$fit, lg_fit2$fit)
+compare_log_model
+```

### 2021-11-03 code/analysis_code/exploratory.Rmd
Part 3 continued. Reorganized the whole "Project" folder".

@@
 
+#MAin outcome variable
+```{r}
+summary(data1$infection_status_info)
+```
+
 #check if certain column is factor or not
 ```{r}
-is.factor(data1$Sex)
+is.factor(data1$infection_status_info)
+```
+
+#plotting infection_status_info count
+```{r}
+plot1 <- ggplot(data = data1) +
+    geom_bar(mapping = aes(x = infection_status_info))
+plot1
+figure_file = here("results","infection_status_info_distribution.png")
+ggsave(filename = figure_file, plot=plot1) 
 ```

### 2021-11-03 code/processing_code/processingscript.Rmd
Part 3 continued. Reorganized the whole "Project" folder".

@@
 ```{r}
-processeddata <- rawdata %>% rename ("education" = `Highest educational level`,
+processeddata1 <- rawdata %>% rename ("education" = `Highest educational level`,
                                "student/heathworker" = `Are you a student or worker in the healthcare sector?`,
@@
 
+```{r}
+processeddata<- processeddata1 %>% mutate(across(where(is_character),as_factor))
+```
+
+```{r}
+View(processeddata)
+```
+
+```{r}
+str(processeddata)
+```
+
 # location to save file
@@
 ```
-
-```{r}
-processeddata2 <- processeddata %>%
-                  mutate (infection_status_info = factor(infection_status_info)) 
-```
-
-```{r}
-str(processeddata2)
-```
-
-```{r}
-save_data_location <- here::here("data","processed_data","processeddata2.rds")
-```
-
-```{r}
-saveRDS(processeddata, file = save_data_location)
-```

### 2021-11-03 products/manuscript/Manuscript.Rmd
Part 3 continued. Reorganized the whole "Project" folder".

--- 2021-10-27 products/manuscript/Manuscript.Rmd
@@
 
-The structure below is a possible setup for a data analysis project (including the course project). For a manuscript, adjust as needed.
-
 # Summary/Abstract
-_Write a summary of your project._
+I'll write it later.,
 
@@
 
-_Study design, sample, and procedure_
+_**Study design, sample, and procedure**_
 
@@
 
-_Measures_
+_**Measures**_
 Using Andersen’s model of health care utilization [Andersen 1995], study variables will be categorized into outcome variable, predisposing factors, enabling/disabling factors and need for care factors.
 
-_Outcome variable_
+_**Outcome variable**_
 COVID-19 testing/infection status will be assessed with the question, “Since the beginning of the COVID-19 outbreak, do you have information on your infection status?” Response options were 1=not tested/does not know test results, 2=negative, and 3=positive.
 
-_Predisposing factors_
+_**Predisposing factors**_
 Sociodemographic factors included age, sex, country of residence, educational level, and the (estimated) age(s) of their housemate(s).
@@
 
-_COVID-19 preventive measures_
+_**COVID-19 preventive measures**_
 Participants were asked, “During the past 7 days, have you been observing any of the following preventive measures against COVID-19?
@@
 
-_Enabling/disabling factors_
+_**Enabling factors**_
 Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel.
 
-_Disabling factors_ include the assessment of psychological distress with the Patient Health Questionnaire (PHQ-4) for Depression and Anxiety symptoms [Kroenke/ Löwe].
-The severity of psychological distress is categorized as normal (0-2), mild (3-5).
-moderate (6-8) and severe (9-12) based on the PHQ-4 scores.
+_**Need for care factors**_ include two questions on 1) the level of fear/worry of being infected with COVID-19 (ranging from 1=not at all worried to 5=extremely worried), and 2) having been quarantined (either at home or elsewhere) at any point in time during the COVID-19 epidemic.
 
-_Need for care factors_ include two questions on 1) the level of fear/worry of being infected with COVID-19 (ranging from 1=not at all worried to 5=extremely worried), and 2) having been quarantined (either at home or elsewhere) at any point in time during the COVID-19 epidemic.
-
-_Data analysis_
+_**Data analysis**_
 
@@
 
-## Data import and cleaning_ [Here I mostly covered descriptive analysis]
+## Data import and cleaning_ html_document
 ---
-title: "try"
-author: "Ehsan"
-date: "10/6/2021"
-output: html_document
----
-
+```{r}
+library(here)
+```
 ## Exploratory analysis
 
-_Use a combination of text/tables/figures to explore and describe your data.
-You should produce plots or tables or other summary quantities for the most interesting/important quantities in your data.
-Depending on the total number of variables in your dataset, explore all or some of the others.
-FIgures produced here might be histograms or density plots, correlation plots, etc.
-Tables might summarize your data._
+As the infection status information of the participants is the main outcome variable, let's see its distribution among the participants:
 
-_Continue by creating plots or tables of the outcome(s) of interest and the predictor/exposure/input variables you are most interested in.
-If your dataset is small, you can do that for all variables.
-Plots produced here can be scatterplots, boxplots, violinplots, etc.
-Tables can be simple 2x2 tables or larger ones._
+```{r resultfigure,  fig.cap='Infection Status Information.', echo=FALSE}
+knitr::include_graphics("../../results/infection_status_info_distribution.png")
+```
 
-_To get some further insight into your data, if reasonable you could compute simple statistics (e.g.
-t-tests, simple regression model with 1 predictor, etc.) to look for associations between your outcome(s) and each individual predictor variable.
-Though note that unless you pre-specified the outcome and main exposure, any "p<0.05 means statistical significance" interpretation is not valid._
+Among the participants, **78.9%** are less than or equal  to 35 years old.
+That indicates that majority of the participants tend to be younger.
+While **45.18%** of the participants were female, **54.82%** were male, which shows less chance of biad due to sex.
+**78.05%** of the participants had a bachelor or post-bachelor degree, clearly indicating that majority of the participants had pretty good education background.
+Almost **50%** of the participants belongs to "upper middle income category", indicating that at least half of the participants don't belong to the poorer side.
+Less than **10%** of the participants live in a village/rural area.
+Health professionals and Tv/radio seems to be the most trusted source to the participants.
+Apparently equal half of the participants worked from home or not at some stage of the study.
+Major half of the participants did quarantine at some stage during the study.
+**63%** of the participants didn't go through a COVID test.
+Almost half of the participants **(46%)** were moderate or more worried about reinfection.
+Only **22%** of the participants recorded to have some sort of chronic disease.
+**(This data can be accessed/viewd through the "supplementary.rmd" file)**
 
-Table \@ref(tab:summarytable) shows a table summarizing the data.
+Let's look at the logistic regression analysis and its statistics summary between the **outcome variable** (infection status info) and the three key **predisposing factors** (Age, Sex, Education level).
+```{r summarytable12,  echo=FALSE}
+resulttable=readRDS("../../results/lg_fit_table_predisposing.rds")
+knitr::kable(resulttable, caption = "logistic regression betweem infection status and Key Predisposing Factors")
+```
+
+```{r summarytable13,  echo=FALSE}
+resulttable=readRDS("../../results/lg_fit_statistics_predisposing.rds")
+knitr::kable(resulttable, caption = "logistic regression statistics betweem infection status and Key Predisposing Factors")
+```
+
+Next, we want to see the logistic regression analysis statistics between the **outcome variable** (infection status info) and the three key **enabling factors** (socio economic status, area of residence,student/healthworker, source of covid news).
+
+```{r summarytable14,  echo=FALSE}
+resulttable=readRDS("../../results/lg_fit_table_enabling.rds")
+knitr::kable(resulttable, caption = "logistic regression  betweem infection status and Key Enabling Factors")
+```
+
+```{r summarytable15,  echo=FALSE}
+resulttable=readRDS("../../results/lg_fit_statistics_enabling.rds")
+knitr::kable(resulttable, caption = "logistic regression statistics betweem infection status and Key enabling Factors")
+```
+
+Next, we want to see the logistic regression analysis statistics between the **outcome variable** (infection status info) and the level of fear of infection and quarantined or not **(Key need for care factors )**
+
+```{r summarytable16,  echo=FALSE}
+resulttable=readRDS("../../results/lg_fit_table_needforcare.rds")
+knitr::kable(resulttable, caption = "logistic regression  betweem infection status and Key Need for care Factor")
+```
+
+```{r summarytable17,  echo=FALSE}
+resulttable=readRDS("../../results/lg_fit_statistics_needforcare.rds")
+knitr::kable(resulttable, caption = "logistic regression statistics betweem infection status and Key Need for Care Factors")
+```
 
@@
 
-Note that this cited reference will show up at the end of the document, the reference formatting is determined by the CSL file specified in the YAML header.
-Many more style files for almost any journal [are available](https://www.zotero.org/styles).
-You also specify the location of your bibtex reference file in the YAML.
-You can call your reference file anything you like, I just used the generic word `references.bib` but giving it a more descriptive name is probably better.
-
 # References

### 2021-11-03 products/manuscript/supplementary.Rmd
Part 3 continued. Reorganized the whole "Project" folder".

---
title: "supplementary"
author: "Ehsan"
date: "11/3/2021"
output: html_document
---

```{r summarytable,  echo=FALSE}
resulttable=readRDS("../../results/summarytable.rds")
knitr::kable(resulttable, caption = 'Age Percentage of Participants.')
```
**78.9% of total participants are less than or equal  to 35 years old.**

```{r summarytable2,  echo=FALSE}
resulttable=readRDS("../../results/summarytable2.rds")
knitr::kable(resulttable, caption = 'Sex Percentage of Participants.')
```
**While 45.18% of the participants were female, 54.82% were male.**

```{r summarytable3,  echo=FALSE}
resulttable=readRDS("../../results/summarytable3.rds")
knitr::kable(resulttable, caption = 'Education Background Percentage of Participants.')
```
**78.05% of the participants had a bachelor or post-bachelor degree**
```{r summarytable4,  echo=FALSE}
resulttable=readRDS("../../results/summarytable4.rds")
knitr::kable(resulttable, caption = 'Income Percentage of Participants.')
```
**Almost 50% of the participants belongs to "upper middle income category"**
```{r summarytable5,  echo=FALSE}
resulttable=readRDS("../../results/summarytable5.rds")
knitr::kable(resulttable, caption = 'Residence Percentage of Participants.')
```
**Less than 10% of the participants live in a village/rural area**
```{r summarytable6,  echo=FALSE}
resulttable=readRDS("../../results/summarytable6.rds")
knitr::kable(resulttable, caption = 'Source of information Percentage of Participants.')
```
**Health professionals and Tv/radio seems to be the most trusted source to the participants.**
```{r summarytable7,  echo=FALSE}
resulttable=readRDS("../../results/summarytable7.rds")
knitr::kable(resulttable, caption = 'Percentage of Participants working from home or not.')
```
**Apparently equal half of the participants worked from or not**
```{r summarytable8,  echo=FALSE}
resulttable=readRDS("../../results/summarytable8.rds")
knitr::kable(resulttable, caption = 'Percentage of Participants quarantined or not at some stage.')
```
**Major half of the participants did quarantine at some stage during the study**
```{r summarytable9,  echo=FALSE}
resulttable=readRDS("../../results/summarytable9.rds")
knitr::kable(resulttable, caption = 'Percentage of covid test status of the participants.')
```
**63% of the participants didn't go through a COVID test**
```{r summarytable10,  echo=FALSE}
resulttable=readRDS("../../results/summarytable10.rds")
knitr::kable(resulttable, caption = "Percentage of participants' worry level about (re)infection with COVID-19.")
```
**Almost half of the participants (46%) were moderate or more worried about reinfection**
```{r summarytable11,  echo=FALSE}
resulttable=readRDS("../../results/summarytable11.rds")
knitr::kable(resulttable, caption = "Percentage of participants' history of chronic disease")
```
**Only 22% of the participants recorded to have some sort of chronic disease**

### 2021-11-03 code/analysis_code/exploratory.Rmd
more edit of exploratory

--- 2021-10-28 code/analysis_code/exploratory.Rmd
@@
 
-#check if certain column is factor or not
+#Summary for the main outcome variable
 ```{r}
-is.factor(data1$Sex)
+summary(data1$infection_status_info)
+```
+
+#check if this column is a factor or not
+```{r}
+is.factor(data1$infection_status_info)
+```
+
+#plotting infection_status_info count and save the result
+```{r}
+plot1 <- ggplot(data = data1) +
+    geom_bar(mapping = aes(x = infection_status_info))
+plot1
+figure_file = here("results","infection_status_info_distribution.png")
+ggsave(filename = figure_file, plot=plot1) 
 ```
@@
 ```
-#the mean age and SD of mean age:
+#Let's find the mean age and SD of mean age:
 ```{r}
@@
 ```
-#people below 35
+#what's the percantage of people below 35 among the participants?
 ```{r}
@@
 ```
-#percentage of male and female
+#percentage of male and female among the participants
 ```{r}
@@
 
-#number of people for each educational category
+#what is the number of people for each educational category among the participants?
 ```{r}
@@
 ```
-#percentage of people for each student category
+#what is the percentage of people for each eductaion category among the participants?
 ```{r}
@@
 
-#student/worker in the heathcare sector?
+#number of student/worker in the heathcare sector among the participants?
 ```{r}
-table(data1$`student/heathworker`)
+summary(data1$`student/heathworker`)
 ```
 
-#percentage of student/health worker
+#percentage of student/health worker among participants?
 
@@
 
-#household members?
+#household members for each participants?
 ```{r}
@@
 ```
+
+#What is the number of participants for each type of economic status?
 ```{r}
-table(data1$`economic_status`)
+summary(data1$`economic_status`)
 ```
@@
 
-#percentage of income category?
+#what is percentage of each income category?
 ```{r}
@@
 
+#what is the number of participants living in different residence setup?
 ```{r}
-table(data1$`residence`)
+summary(data1$`residence`)
 ```
+
 ```{r}
@@
 
+#what source the trust the most for COVID-related information?
 ```{r}
@@
 ```
-#most trusted source?
+#percentage of most trusted source?
 ```{r}
@@
 
-#percentage of work from home or not?
+#percentage of participants work from home or not?
 ```{r}
@@
 
-#Descriptive analysis for each question?
+#number of participants who quarantined or not?
 ```{r}
@@
 ```
-#Quarantined or not
+#Percentage of participants Quarantined or not
 ```{r}
@@
 
+#number of people with their respective infection status?
 ```{r}
@@
 ```
-#correct knowledge of their status
+#correct knowledge of their status with the percentage?
 ```{r}
@@
 
+#the next code basically summarizes the answers for each question:
 ```{r}

### 2021-11-11 code/analysis_code/analysisscript.Rmd
table

@@
 library(broom.mixed)
+library(table1)
 library(here)
@@
 mydata <- readRDS(data_location)
-glimpse(mydata)
+View(mydata)
+```
+
+#get a table
+```{r}
+overall_summary <- table1(~ Age + Sex + education + economic_status + student_or_heathworker + residence + trusted_source + work_from_home + quarantined_or_not + infection_status_info + worry_level + chronic_disease_history + social_distance_practice + follow_preventive_measure   , data=mydata, overall="Total")
+overall_summary
+```
+```{r}
+df100 = data.frame(overall_summary)
+summarytable_file = here("results", "Overall.rds")
+saveRDS(df100, file = summarytable_file)
 ```

### 2021-11-11 code/processing_code/processingscript.Rmd
table

@@
 processeddata1 <- rawdata %>% rename ("education" = `Highest educational level`,
-                               "student/heathworker" = `Are you a student or worker in the healthcare sector?`,
-                               "economic_status" = 'Which of the following categories best describes your current socio-economic situation?',
+                               "student_or_heathworker" = `Are you a student or worker in the healthcare sector?`,
+                               "economic_status" = `Which of the following categories best describes your current socio-economic situation?`,
                                "residence" = `Do you live in:`,
                                "trusted_source" = `Which source of COVID-19 information/advice do you trust the most?`,
-                               "work_from_home" = 'Are you currently working/studying from home because of the COVID-19 outbreak?',
+                               "work_from_home" = `Are you currently working/studying from home because of the COVID-19 outbreak?`,
                                "quarantined_or_not" = `Have you been quarantined (either at home or else where) at any point in time during the Covid-19 epidemic?`,
                                "infection_status_info" = `Since the beginning of the COVID-19 outbreak, do you have information on your infection status?`,
-                               "worry_level" = `How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5`,)
+                               "worry_level" = `How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5`,
+                               "chronic_disease_history" = `Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above`,
+                              "social_distance_practice" = `During the past 7 days, have you been observing any of the following preventive measures against COVID-19?
+(Tick all answers that apply): Social distancing of at least 1.5m`,
+                              "follow_preventive_measure" = `During the past 7 days, have you been observing any of the following preventive measures against COVID-19?
+(Tick all answers that apply): None of the above`)
 ```

### 2021-11-11 products/manuscript/Manuscript.Rmd
table

@@
 
+```{r summarytable,  echo=FALSE}
+resulttable=readRDS("../../results/Overall.rds")
+knitr::kable(resulttable, caption = "**Overall Descriptive Statistics of the Participants**")
+```
+
 As the infection status information of the participants is the main outcome variable, let's see its distribution among the participants:
@@
 Only **22%** of the participants recorded to have some sort of chronic disease.
-**(This data can be accessed/viewd through the "supplementary.rmd" file)**
+**(Separate analysis for each variable was done and the data can be accessed/viewd through the "supplementary.rmd" file)**
 

### 2021-11-12 code/analysis_code/analysisscript.Rmd
Referencing done!

@@
 mydata <- readRDS(data_location)
-View(mydata)
+```
+
+#outcome split
+```{r}
+mydata$infection_status_info %>% table()
 ```
@@
 ```
+
+#we want to predict each infection status level, not a single contrast.
+It was a bit difficult to figure out how to do this, but one needs to search here for the model to find the function one needs, turns out it is called multinom_reg()
+
+#make a recipe
+
+```{r}
+mydata_recipe <- 
+  recipe(infection_status_info ~ Age + Sex + education + economic_status + student_or_heathworker + residence + trusted_source + work_from_home + quarantined_or_not + infection_status_info + worry_level + chronic_disease_history + social_distance_practice + follow_preventive_measure, data = mydata)
+```
+
+#make a model
+#choose multinom_reg() + nnet
+```{r}
+mydata_model <- 
+  multinom_reg() %>% 
+  set_engine("nnet")
+```
+
+#resampling method
+```{r}
+set.seed(200)
+mydata_folds <- vfold_cv(mydata, v = 10)
+```
+
+#make workflow
+```{r}
+mydata_wf <- 
+  workflow() %>% 
+  add_model(mydata_model) %>% 
+  add_recipe(mydata_recipe)
+```
+
+#fit
+```{r}
+mydata_fit <- 
+ mydata_wf %>% 
+  fit_resamples(mydata_folds)
+```
+
+#metrics
+```{r}
+collect_metrics(mydata_fit)
+```

### 2021-11-12 code/analysis_code/more.Rmd
Referencing done!

--- 2021-11-12 code/analysis_code/analysisscript.Rmd
@@
+---
 ---
@@
 library(dotwhisker)
-library(broom.mixed)
+library(broom)
 library(table1)
 library(here)
+library(nnet)
+library(patchwork)
+library(knitr)
+library(GGally)
+library(pacman)
+library(dplyr)
 ```
@@
 mydata <- readRDS(data_location)
+View(mydata)
 ```
@@
 ```
-
-#get a table
-```{r}
-overall_summary <- table1(~ Age + Sex + education + economic_status + student_or_heathworker + residence + trusted_source + work_from_home + quarantined_or_not + infection_status_info + worry_level + chronic_disease_history + social_distance_practice + follow_preventive_measure   , data=mydata, overall="Total")
-overall_summary
-```
-```{r}
-df100 = data.frame(overall_summary)
-summarytable_file = here("results", "Overall.rds")
-saveRDS(df100, file = summarytable_file)
-```
-
-#The main "outcome variable" is the knowledge of infection status (positive/negative/not tested).
-There are "predisposing factors" (age, sex, education level, chronic disease history etc), "enabling factors" (socio-economic status, area of residence, source of covid news etc) and "need for care factors" (level of fear of reinfection, quarantined or not).
-We'll do logistic regression analysis for key factors of epredisposing, enabling and need for care factors.
-
-#We'll start with logistic regression model betweem infection status and Age, Sex, Education level (Key Predisposing Factors)
-```{r}
-lg_mod <- 
-       logistic_reg() %>% 
-       set_engine("glm")
-lg_fit <-
-       lg_mod %>%
-       fit(infection_status_info ~ Age + Sex + education, data = mydata)
-lg_fit
-```
-
-```{r}
-tidy(lg_fit)
-```
-
-```{r}
-lg_fit_table_predisposing <- tidy(lg_fit)
-```
-
-# saved it as a file
-```{r}
-summarytable_file12 = here("results", "lg_fit_table_predisposing.rds")
-saveRDS(lg_fit_table_predisposing, file = summarytable_file12)
-```
-
-```{r}
-glance(lg_fit)
-```
-
-```{r}
-lg_fit_statistics_predisposing <- glance(lg_fit)
-```
-
-# saved it as a file
-```{r}
-summarytable_file13 = here("results", "lg_fit_statistics_predisposing.rds")
-saveRDS(lg_fit_statistics_predisposing, file = summarytable_file13)
-```
-
-#Then, we'll do log model betweem infection status and socio economic status, area of residence,student/healthworker, source of covid news (Key enabling Factors)
-```{r}
-lg_fit1 <-
-       lg_mod %>%
-       fit(infection_status_info ~ economic_status + residence + trusted_source , data = mydata)
-lg_fit1
-```
-
-```{r}
-tidy(lg_fit1)
-```
-
-```{r}
-lg_fit_table_enabling <- tidy(lg_fit1)
-```
-
-# saved it as a file
-```{r}
-summarytable_file14 = here("results", "lg_fit_table_enabling.rds")
-saveRDS(lg_fit_table_enabling, file = summarytable_file14)
-```
-
-```{r}
-glance(lg_fit1)
-```
-
-```{r}
-lg_fit_statistics_enabling <- glance(lg_fit1)
-```
-
-# saved it as a file
-```{r}
-summarytable_file15 = here("results", "lg_fit_statistics_enabling.rds")
-saveRDS(lg_fit_statistics_enabling, file = summarytable_file15)
-```
-
-#Then, we'll do log model betweem infection status and level of fear of infection and quarantined or not (Key need for care factors )
-```{r}
-lg_fit2 <-
-       lg_mod %>%
-       fit(infection_status_info ~ quarantined_or_not + worry_level , data = mydata)
-lg_fit2
-```
-
-```{r}
-tidy(lg_fit2)
-```
-
-```{r}
-lg_fit_table_needforcare <- tidy(lg_fit2)
-```
-
-# saved it as a file
-```{r}
-summarytable_file16 = here("results", "lg_fit_table_needforcare.rds")
-saveRDS(lg_fit_table_needforcare, file = summarytable_file16)
-```
-
-```{r}
-glance(lg_fit2)
-```
-
-```{r}
-lg_fit_statistics_needforcare <- glance(lg_fit2)
-```
-
-# saved it as a file
-```{r}
-summarytable_file17 = here("results", "lg_fit_statistics_needforcare.rds")
-saveRDS(lg_fit_statistics_needforcare, file = summarytable_file17)
-```
-
-#compare three models
-```{r}
-compare_log_model <- anova(lg_fit$fit, lg_fit1$fit, lg_fit2$fit)
-compare_log_model
-```
-
-#we want to predict each infection status level, not a single contrast.
-It was a bit difficult to figure out how to do this, but one needs to search here for the model to find the function one needs, turns out it is called multinom_reg()
 

### 2021-11-12 code/processing_code/processingscript.Rmd
Referencing done!

@@
 processeddata1 <- rawdata %>% rename ("education" = `Highest educational level`,
+                                      "serial" = `Serial number`,
                                "student_or_heathworker" = `Are you a student or worker in the healthcare sector?`,

### 2021-11-12 products/manuscript/Manuscript.Rmd
Referencing done!

@@
 
+Testing can help people determine if they are infected with SARS-CoV-2 – regardless of whether they have symptoms – and whether they are at risk of spreading the infection to others.
+Testing of all people for SARS-CoV-2, including those who have no symptoms, who show symptoms of infection, and who may have been exposed to the virus can help prevent the spread of COVID-19 and identify people in need of care in a timely fashion.
+A positive test early in the course of the illness enables individuals to isolate themselves – reducing the chances of infecting others and allowing them to seek treatment earlier, likely reducing disease severity and the risk of long-term disability, or death.
+
+A negative test does not mean the person will not be able to acquire and transmit the infection in the future.
+Therefore, even if an individual is test negative, continuation of hygiene practices to self-protect and others by washing hands with soaps/ sanitizers frequently, physical distancing, and wearing a face mask is required.
+A positive test means isolation is mandatory, and that others with whom the individual may have been in contact since the time of exposure should also get tested.
+Since it is recognized that nearly half of all SARS-CoV-2 infections are transmitted by pre-symptomatic and asymptomatic people, identifying infected individuals while they are pre-symptomatic, as well as those who are asymptomatic, will play a major role in containing the pandemic.
+
+Scanty research has been conducted to identify factors associated with the uptake of COVID-19 testing.
+In a cross-sectional community survey in Ontario, Canada, 3.3% tested positive for SARS-CoV-2.
+The odds of being tested increased with age, male sex, several underlying health conditions, previous use of health care services, and higher household income [@SundaramE].
+Comparing the odds of COVID-19 positive diagnosis with test-negatives and untested individuals, older age, certain comorbidities, such as hypertension, diabetes and heart diseases, higher previous use of health care services were associated with increased odds of a positive SARS-CoV-2 test result [@SundaramE].
+Using UK biobank data, being tested for COVID-19 was associated with male sex, Black ethnicity, lower socioeconomic status, occupation (being a health care worker, retired, unemployed), ever smoker, comorbidities, and exposure to particulate matter (PM) 2.5 absorbance [@Chadeau-hyam].
+Among tested individuals, only male sex, non-White ethnicity, and lower education and none of the comorbidities or health risk factors were associated with a COVID-19 positive diagnosis [Chadeau-Hyam].
+Workers in the healthcare sector are also at a higher risk of testing positive.
+A meta-analytic study showed that the pooled prevalence of healthcare workers testing positive for COVID-19 was between 7 to 11% [@Gomez-Ochoa].
+
 ## General Background Information
@@
 _**Measures**_
-Using Andersen’s model of health care utilization [Andersen 1995], study variables will be categorized into outcome variable, predisposing factors, enabling/disabling factors and need for care factors.
+Using Andersen’s model of health care utilization , study variables will be categorized into outcome variable, predisposing factors, enabling/disabling factors and need for care factors.
 
@@
 _**Enabling factors**_
-Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel.
+Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel[@Bono].
 
@@
 
-_Include citations in your Rmd file using bibtex, the list of references will automatically be placed at the end_
-
-This paper [@Leek2015a] discusses types of analyses.
-
 # References

### 2021-11-12 code/analysis_code/analysisscript.Rmd
Referencing Completed!

@@
 ```
+
 ```{r}
@@
 
-#make a recipe
-
-```{r}
-mydata_recipe <- 
-  recipe(infection_status_info ~ Age + Sex + education + economic_status + student_or_heathworker + residence + trusted_source + work_from_home + quarantined_or_not + infection_status_info + worry_level + chronic_disease_history + social_distance_practice + follow_preventive_measure, data = mydata)
-```
-
 #make a model
@@
 
-#resampling method
+#make a recipe
+
 ```{r}
-set.seed(200)
-mydata_folds <- vfold_cv(mydata, v = 10)
+mydata_recipe <- 
+  recipe(infection_status_info ~ Age + Sex + education + economic_status + student_or_heathworker + residence + trusted_source + work_from_home + quarantined_or_not + infection_status_info + worry_level + chronic_disease_history + social_distance_practice + follow_preventive_measure, data = mydata)
+```
+
+# Put 70% of the data into the training set and 30% into testing using strata=BodyTemp
+```{r}
+data_split <- initial_split(mydata, prop = 0.7, strata = infection_status_info)
+```
+
+# Create data frames for the two sets:
+```{r}
+train_data <- training(data_split)
+test_data  <- testing(data_split)
+```
+
+# training set proportions by class
+```{r}
+train_data %>% 
+  count(infection_status_info) %>% 
+  mutate(prop = n/sum(n))
+```
+
+# test set proportions by class
+```{r}
+test_data %>% 
+  count(infection_status_info) %>% 
+  mutate(prop = n/sum(n))
+```
+##5-fold cross validation, 5 times repeated, stratified on `infection status` for the CV folds
+```{r}
+mydata_folds <- vfold_cv(train_data, v = 5, repeats =5, strata= "infection_status_info")
 ```

### 2021-11-13 code/analysis_code/analysisscript.Rmd
Further Analysis completed

@@
 
-# saved it as a file
+#saved it as a file
 ```{r}
@@
 
+#**Analysis for Part 4 starts here**  
 #make a model
@@
 
-# Put 70% of the data into the training set and 30% into testing using strata=BodyTemp
+#Put 70% of the data into the training set and 30% into testing using strata=BodyTemp
 ```{r}
@@
 
-# Create data frames for the two sets:
+#Create data frames for the two sets:
 ```{r}
@@
 
-# training set proportions by class
+#training set proportions by class
 ```{r}
@@
 
-# test set proportions by class
+#test set proportions by class
 ```{r}
@@
 ```
-##5-fold cross validation, 5 times repeated, stratified on `infection status` for the CV folds
+##5-fold cross validation, 5 times repeated, stratified on `infection status` for the CV folds with training data
 ```{r}
@@
 
-#fit
+#fitting the training data
 ```{r}
-mydata_fit <- 
+training_data_fit <- 
  mydata_wf %>% 
@@
 
-#metrics
+#metrics of training data
 ```{r}
-collect_metrics(mydata_fit)
+collect_metrics(training_data_fit)
 ```
+##5-fold cross validation, 5 times repeated, stratified on `infection status` for the CV folds with test data
+```{r}
+mydata_folds2 <- vfold_cv(test_data, v = 5, repeats =5, strata= "infection_status_info")
+```
+#fitting the test data
+```{r}
+test_data_fit <- 
+ mydata_wf %>% 
+  fit_resamples(mydata_folds2)
+```
+
+#metrics of test data
+```{r}
+collect_metrics(test_data_fit)
+```

### 2021-11-13 code/analysis_code/exploratory.Rmd
Further Analysis completed

@@
 data1 %>% 
-     group_by( `student/heathworker` ) %>% 
+     group_by( `student_or_heathworker` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
@@
 chronic_disease_history = data1 %>% 
-     group_by( `Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above` ) %>% 
+     group_by( `chronic_disease_history` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )
@@
 ```{r}
-table(data1$`During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Social distancing of at least 1.5m`)
+table(data1$`social_distance_practice`)
 ```
@@
 data1 %>% 
-     group_by( `During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): None of the above` ) %>% 
+     group_by( `follow_preventive_measure` ) %>% 
      summarise( percent = 100 * n() / nrow( data1) )

### 2021-11-13 code/analysis_code/analysisscript.Rmd
Manuscript Updated!

@@
 author: "Ehsan"
-date: "10/27/2021"
+date: "11/12/2021"
 output: html_document
@@
 
+#saved it as a file
+```{r}
+summarytable_file18 = here("results", "Comparison of Models.rds")
+saveRDS(compare_log_model, file = summarytable_file18)
+```
 #we want to predict each infection status level, not a single contrast.
@@
 ```{r}
-collect_metrics(training_data_fit)
+training_data_metrics <- collect_metrics(training_data_fit)
+training_data_metrics
 ```
+#saved it as a file
+```{r}
+summarytable_file19 = here("results", "Metrices of Training Data.rds")
+saveRDS(training_data_metrics, file = summarytable_file19)
+```
+
 ##5-fold cross validation, 5 times repeated, stratified on `infection status` for the CV folds with test data
@@
 ```{r}
-collect_metrics(test_data_fit)
+test_data_metrics <- collect_metrics(test_data_fit)
+test_data_metrics
 ```
+#saved it as a file
+```{r}
+summarytable_file20 = here("results", "Metrices of TestData.rds")
+saveRDS(test_data_metrics, file = summarytable_file20)
+```

### 2021-11-13 products/manuscript/Manuscript.Rmd
Manuscript Updated!

@@
 
+The comparison between these three models give us this information:
+
+```{r summarytable18,  echo=FALSE}
+resulttable=readRDS("../../results/Comparison of Models.rds")
+knitr::kable(resulttable, caption = "Comparison of the Models")
+```
+
+we want to predict each infection status level, not a single contrast by using multinom_reg(). The result is as following:
+
+```{r summarytable19,  echo=FALSE}
+resulttable=readRDS("../../results/Metrices of Training Data.rds")
+knitr::kable(resulttable, caption = "Metrices of Training Data")
+```
+
+```{r summarytable20,  echo=FALSE}
+resulttable=readRDS("../../results/Metrices of TestData.rds")
+knitr::kable(resulttable, caption = "Metrices of Testing Data")
+```
+
 # Discussion

### 2021-12-03 products/manuscript/Manuscript.Rmd
Updated after Dawson's eval!

@@
 # Summary/Abstract
-I'll write it later.,
+**Objective:** The COVID-19 testing situation in Bangladesh was controlled with various social measures.
+Much of the information covered in the media and in studies focused on the public health and economic aspects of the pandemic.
+This study aimed to explore the testing decision influences of  adult people, which is important especially in an young society categorised as low income or middle income due to the limits of economic and healthcare resources.
+
+**Setting:** The impact of COVID-19 on adult persons in Bangladesh, an online survey, taken across the six regions of the country.
+
+**Participants:** Total 759 adults (median age 45 years, interquartile range 33-57 years, range 18-93 years), participated in the study. COVID-19 testing/infection status was assessed by self-report.
+
+**Outcome measures:** The analysis focused on the the knowledge of young adults of their infection status based on testing during the pandemic using logistic regression analysis.
+
+_Results:_
+
+**Conclusion:** Observing the status of the infection knowledge of the adult population is important for introducing policies that can improve their decision on testing.
+
+**Keywords:** COVID-19; public health; social medicine.
 
@@
 ## Strengths and Limitations
-_Discuss what you perceive as strengths and limitations of your analysis._
+Our study respondents cannot be considered representative of the general population in the study country, since respondents needed to have had access to the internet to participate in the online survey.
+Moreover, self-reports, including the outcome variable COVID-19 testing, may be influenced by recall bias and social desirability.
+We also have no information on the type of test used for COVID-19 testing, limiting the accuracy and authenticity of the test results.
+Some variables, such as COVID-19 symptoms, previous use of health care services, obesity, and smoking, that have been found affecting COVID-19 testing uptake [@Chadeau-hyam] were not assessed in this survey and should be included in future studies.
 
 ## Conclusions
-_What are the main take-home messages?_
+This study among adults across Bangladesh reported a high prevalence of COVID-19 testing.
+Factors associated with COVID-19 testing included some predisposing factors (residing , postgraduate education, having at least one chronic condition) and enabling/disabling factors (urban residence, higher perceived economic status, being a student or worker in the health care sector, and moderate or severe psychological distress).
+Identified predisposing and enabling or disabling factors can be used to design programmes to improve COVID-19 testing uptake.
+Access to testing needs to be increased for persons living in Bangladesh and similar resource poor settings.
+In addition, COVID-19 testing programs need to target persons of lower economic status and of lower education level who currently less tested but most at risk for COVID-19 infection.
 

### 2021-12-10 Reviews/Project_Review_DDobash_to_ESuez.Rmd
Final update!

---
title: Project Review by Dawson Dobash for Ehsan Suez
date: "`r file.mtime(knitr::current_input())`"
#bibliography: ../media/references.bib
output: 
  html_document:
    toc_depth: 3
    number_sections: true
---

# Overview

Title of project:

Name of project author(s): Ehsan Suez

Name of project reviewer: Dawson Dobash

# Specific project content evaluation
Evaluate the different parts of the project by filling in the sections below.

## Background, Context and Motivation
How well is the context of the project described? Is a comprehensive background, including summary of previous/related work given? Is the project well placed into the context of existing work (including proper referencing of existing work). Is it clear why the project was undertaken and what new information it hopes to provide?

### Feedback and Comments

For your introduction, I would say some parts of it got wordy and sometimes hard to understand when you were listing factors from other studies. You did provide some good previous/related work within your introduction. The project is well placed as you are doing another study as the ones you've describe but within another country. The new information comes from using Andersen's model of health care utilization. I guess my comment would be what information would be coming out from this analysis specifically what impact will this have to Bangladesh if they see your results? Would they try to promote more tests for a specific group of people?

### Summary assessment (PICK ONE, DELETE THE OTHERS)
* strong contextualization and motivation

## Question description
How well and clear are the question(s)/hypotheses the project aims to address described? Is it clear how the questions relate to the data?

### Feedback and Comments

Yes it is clear what the question is and how it is related to the data. A stylistic change I would do is just present your question different such as just saying the question as a direct statement.

### Summary assessment
* question/hypotheses fully clear

## Data description
How well is the data overall described? Is the source provided? Is a codebook or other meta-information available that makes it clear what the data is?

### Feedback and Comments

I would put the source of your data somewhere within your Description of data and data source section (2.2). I know you mentioned an online survey but what online survey and where is this online survey located. I see that within the Methods and Results section (3), you explain the data more there. I would move those descriptions of the data to the Description of data and data source section (2.2). You explain the levels of each variable which is good.

### Summary assessment
* source and overall structure of data somewhat explained

## Data wrangling and exploratory analysis
How well is the data cleaned/processed and explored? Are all steps reasonable and well explained? Are alternatives discussed and considered? Are meaningful exploratory results shown (e.g. in the supplementary materials)?

### Feedback and Comments

I think the data is clean because it is a survey which means each observation tends to one person but not too much cleaning was done. For the exploratory analysis, I only see two things in the manuscript for exploratory analysis which one is a large table. I dont know how much other information from your exploratory file you might want to add if it looks maybe interesting, I would include it. I would look through and see what else you could include but remember to limit it in the manuscript. Also there is no separate section for the main analysis. I would include more of a description to your methods section, and include your newest tests you have done from the analysis script.

### Summary assessment
* some weaknesses in wrangling and exploratory component

## Appropriateness of Analysis
Were the analysis methods appropriate for the data? Was the analysis done properly? Were different components of the analysis (e.g. performance measure, variable selection, data pre-processing, model evaluation) done in the best way possible and explained well?

### Feedback and Comments

From what I can tell, it looks like the analysis was done properly. You just need to include the final part of your analysis to the manuscript from the analysis script. Since it is not part of the manuscript as of now and you have not explained it yet, that is the only reason I will be giving you the summary assessment I am giving you. You could try the other machine learning techniques just to see what results you get comparing to the other technique you used.

### Summary assessment
* defensible but not optimal analysis

## Presentation
How well are results presented? Are tables and figures easy to read and understand? Are the main figures/tables publication level quality?

### Feedback and Comments

Some results are missing, the tables are sometimes hard to understand (I also have a similar problem with my project), and the figure could have better descriptions (x-axis and main title). I would recommend adding more commentary to what your analyses mean, explain each table, and reference the figure and tables while describing their results such as "In Table [blank],...". JUst make sure it is clear what table/figure you are referencing to and the results you want to present is clearly explained and limit the complex sentence structure when explaining the results.

### Summary assessment
* results are poorly presented, hard to understand, poor quality

## Discussion/Conclusions
Are the study findings properly discussed? Are strengths and limitations acknowledged? Are findings interpreted properly?

### Feedback and Comments

You have not finished this area therefore I cannot assess this section.

### Summary assessment
* major parts of discussion missing or wrong

## Further comments

For your supplemental material file, you need to add some more commentary about each thing. For your manuscript, you still need to complete your summary and abstract. You also need to go through your transcript and delete sections that you plan on not writing in such as Data acquisition (3.1) if you plan on using other sections to describe that contents.

# Overall project content evaluation
Evaluate overall features of the project  by filling in the sections below.

## Structure
Is the project well structured? Are files in well labeled folders? Do files have reasonable names? Are all "junk" files not needed for analysis/reproduction removed? By just looking at files and folders, can you get an idea of how things fit together?

### Feedback and Comments

The structure of the project looks like it is good and each file is within its respected and reasonable named folders. Looking through the folders, there are no files that seem out of context but, there are still some junk files/useless files that are from the template still such as slides in the product folder and the analysisscript.R file.

### Summary assessment
* mostly clear, but some confusing parts (e.g. useless files, things in the wrong folders)

## Documentation 
How well is the project documented? Are you able to understand each step of the whole analysis, each decision that was made, and each line of code? Is enough information provided as comments in code or as part of Rmd files?

### Feedback and Comments

I am going to break down the documentation by file. First, within the processing script, it is minor but there is no documentation on the renaming process or the changing to a factor code. But again this is very very minor. Might not need to explain this.

Next within you exploratory file, around line 282, no comments of what these command do. I see if creates a frequencies for each variable but need to explain that. Also although you explained what each code is figuring out, you might want to add some comments on the ways you are displaying it such as "I am using [blank] to show [blank]".

Within the analysis script, similar to the exploratory file, you might want to add more comments on the techniques/functions you used to find the results you have. You explain you are using logistic regression but maybe explain you are getting summary statistics for these models. Also for some of these models, maybe comment on some of the results that you get focusing on the biggest finds.

### Summary assessment
* decently documented with some gaps

## Reproducibility
Are all results fully reproducible? Is documentation provided which clearly explains how to reproduce things, and does it work without the need for any manual intervention? Are you able to re-run the whole analysis without having to do manual interventions/edits?

### Feedback and Comments

All of the documentation and files were full reproducible. Within the main readme file, you mention what each file does but you might want to give some simple steps on what way and order to reproduce everything.

### Summary assessment
* fully reproducible without issues

## Thoroughness
How thorough was the overall study? Were alternatives (e.g. different ways of processing the data or different models) considered? Were alternatives discussed? Were the questions/hypotheses fully and thoroughly addressed?

### Feedback and Comments

It seems like the data was already able to run without too much cleaning to the file, and as for different models, you had to figure out what the best way/the way you want to analyze your data besides the other type we learned in class. For your specific analysis I do not know off the top of my head what other model types you could have used if this specific function was able to run how you wanted to run it.

### Summary assessment
* strong level of thorougness

## Further comments

For your overall content evaluation, it looks like you were organized in your repository. I would say maybe update you read me file specifically when you talked about the analysis script because you also did part 4 analysis.

You are also missing a lot from your manuscript so I would try to finish those areas as soon as possible. I think you project is very interesting and good luck with the rest of the semester. Looking forward to your complete project! GOOD LUCK and I hope I gave you some help!!

### 2021-12-10 Reviews/Project_Review_MChan_to_ESuez.RMD
Final update!

---
title: Project Review Template 
date: "`r file.mtime(knitr::current_input())`"
#bibliography: ../media/references.bib
output: 
  html_document:
    toc_depth: 3
    number_sections: true
---

# Overview

Title of project:"Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in Bangladesh: an online survey"

Name of project author(s): Ehsan Suez

Name of project reviewer: Monica Chan

# Specific project content evaluation

## Background, Context and Motivation
How well is the context of the project described? Is a comprehensive background, including summary of previous/related work given? Is the project well placed into the context of existing work (including proper referencing of existing work). Is it clear why the project was undertaken and what new information it hopes to provide?

### Feedback and Comments
Your background on SARS-CoV2 infection and the data gathered is great.
Unfortunately, I'm unfamiliar with the Andersen's model of health care utilization. 
I think that adding some more details about the Andersen's model of health care utilization would be beneficial since it is part of your title, but not mentioned anywhere else besides you have selected it. Perhaps add some reasoning why you are using this model of healthcare utilization, or expand more on why it is better than others?

### Summary assessment

* strong contextualization and motivation

## Question description
How well and clear are the question(s)/hypotheses the project aims to address described? Is it clear how the questions relate to the data?

To use Andersen's model of health care utilization to determine factors associated with COVID-19 testing among adults in Bangladesh.

### Feedback and Comments

Your question is more of an exploratory analysis and is stated clearly.
I think you could elaborate more on some of the data like what factors out of everything gathered, survey data, or quantitative data were the most impact in association with the COVID-19 testing.

### Summary assessment

* question/hypotheses fully clear

## Data description
How well is the data overall described? Is the source provided? Is a codebook or other meta-information available that makes it clear what the data is?

### Feedback and Comments

A key may be useful witin the repository as part of the readme in the raw data or data folder.
Otherwise the data is expanded on in the manuscript in section 2.2.
The source is well documented in the manuscript and explained more in the introduction, this is fine-- but I feel that the detail about the data in the introduction is a bit too much and would serve better in the 2.2 Description of data and data source.

### Summary assessment

* source and overall structure of data somewhat explained

## Data wrangling and exploratory analysis
How well is the data cleaned/processed and explored? Are all steps reasonable and well explained? Are alternatives discussed and considered? Are meaningful exploratory results shown (e.g. in the supplementary materials)?

### Feedback and Comments

Data wrangling was good in saving the wrangled data in the processed data section to be used in downstream code.
Exploratory results were great at describing the results from the data gathered, but limited to really . I really liked the summary table output in the `analysisscipt` code chunk 5.

### Summary assessment

* some weaknesses in wrangling and exploratory component

## Appropriateness of Analysis
Were the analysis methods appropriate for the data? Was the analysis done properly? Were different components of the analysis (e.g. performance measure, variable selection, data pre-processing, model evaluation) done in the best way possible and explained well?

### Feedback and Comments

I like the analysis stats you have with the intercepts and P-values.

The manuscript is a little conversational, maybe adjust in the paper-- but is fine as comments in the code.

### Summary assessment

* defensible but not optimal analysis

## Presentation
How well are results presented? Are tables and figures easy to read and understand? Are the main figures/tables publication level quality?

### Feedback and Comments

Results and stats are presented. Some text is needed to detail highlights of the results.
Three may be too many stats/results presented, some could possibly be moved to a supplementary folder for additional elaboration that may not be too central to the questions asked.
If possible, I think a good mix of figures in addition to the tables would be great and could make a lot of the descriptive data easily readable.

[Comments after update pull 12/3/2021]
There's not a specific results section. I think some of the exploratory analysis could be split better into a results section or have the exploratory analysis be under a results section

### Summary assessment
* results are poorly presented, hard to understand, poor quality

## Discussion/Conclusions
Are the study findings properly discussed? Are strengths and limitations acknowledged? Are findings interpreted properly?

### Feedback and Comments

Discussion section is not complete. With all the results presented, reminder to justify why certain aspects were chosen and tested.

[Comments after update pull 12/3/2021]
Summary and interpretation needs to be filled in.
Strengths and limitations covers a bit of ground, could always add more.

Conclusion could repeat the primary question and answer directly. Followed by more support sentences.

### Summary assessment
* major parts of discussion missing or wrong

## Further comments

I think the paper would benefit from a pure Results section (difference from actual structure of the paper and the sections outlined in the Summary/Abstract). So maybe think about separating Methods and results into 2 sections.

Create and finalize the final results, discussion, and conclusion sections and I think it should be in good condition.

# Overall project content evaluation

## Structure
Is the project well structured? Are files in well labeled folders? Do files have reasonable names? Are all "junk" files not needed for analysis/reproduction removed? By just looking at files and folders, can you get an idea of how things fit together?

### Feedback and Comments

Structure is easy to follow as it is still structured as the `dataanalsysis-template` for the class.

Primary files are in the correct/expected folders.

[Comments after update pull 12/3/2021]
Files still contain some unused files and folders (see in the products and unused template files). You can make an `ARCHIVED` folder to place all unused files. Alternatively you can just remove them.

### Summary assessment

* mostly clear, but some confusing parts (e.g. useless files, things in the wrong folders)

## Documentation 
How well is the project documented? Are you able to understand each step of the whole analysis, each decision that was made, and each line of code? Is enough information provided as comments in code or as part of Rmd files?

### Feedback and Comments

I like the explanations of why certain things are done, the notation is a little different than what I'm used to (inline comments). They could be expanded more yet the text there can be interpreted as needed.

[Comments after update pull 12/3/2021]
In section 3.2 in the manuscript, I'm not sure if the code chunk is needed to be in this document, or relevant in that one space.

### Summary assessment

* decently documented with some gaps

## Reproducibility
Are all results fully reproducible? Is documentation provided which clearly explains how to reproduce things, and does it work without the need for any manual intervention? Are you able to re-run the whole analysis without having to do manual interventions/edits?

### Feedback and Comments

Code ran and knit with no errors.

### Summary assessment

* fully reproducible without issues

## Thoroughness
How thorough was the overall study? Were alternatives (e.g. different ways of processing the data or different models) considered? Were alternatives discussed? Were the questions/hypotheses fully and thoroughly addressed?

### Feedback and Comments

It's hard to tell with results being difficult to interpret or place in a section that I am unable to recognize as results. There's a lot of observations about the data, which is nice to get a view about the population being looked at.

[Comments after update pull 12/3/2021]
Since the starting question is limited to a specific model from the title and determine factors mentioned specifically in the questions to be addressed-- the study and alternatives are limited.

Discussion needs to be elaborated on, due to how limited the study is/was.

### Summary assessment

* strong level of thoroughness

## Further comments

[Comments after update pull 12/3/2021]
I think you accomplished what you wanted to for this project and for this data set.
I do think that you can improve a bit on the organization of the manuscript. Your abstract section has boded sections, maybe outline the manuscript in that manner and shuffle the subsection under the main sections. to improve clarity and flow of the paper.
Work on the Discussion of results and flush out the strengths/limitations and conclusion sections and it should be good.

### 2021-12-10 products/manuscript/Manuscript.Rmd
Final update!

@@
 
-_Results:_
+**Results:** Of the 759 participants, 37% had tested for COVID-19, 9% tested positive, and 28.0% tested negative.
+In a logistic regression model, predisposing factors (Age, being female, having at least one chronic condition) and enabling/disabling factors (urban residence, higher perceived economic status) increased the odds of COVID-19 testing.
+Among those who were tested, participants residing in Bangladesh, those who had moderate to to severe psychological distress were positively associated with COVID-19 positive diagnosis.
 
@@
 ## Questions/Hypotheses to be addressed
-The main question is to find out the key factors associated with covid-19 testing
+The main question is to find out the key factors associated with covid-19 testing decision.
+There are several predisposing factors, enabling factors, disabling factors, need for care factors and we aim to find out which of them significantly plays a role behind an individual's decision to get tested for covid.
 
@@
 
-_**Study design, sample, and procedure**_
+_**Study design, sample, and procedure:**_
 
@@
 
-_**Measures**_
+_**Measures:**_
 Using Andersen’s model of health care utilization , study variables will be categorized into outcome variable, predisposing factors, enabling/disabling factors and need for care factors.
 
-_**Outcome variable**_
+_**Outcome variable:**_
 COVID-19 testing/infection status will be assessed with the question, “Since the beginning of the COVID-19 outbreak, do you have information on your infection status?” Response options were 1=not tested/does not know test results, 2=negative, and 3=positive.
 
-_**Predisposing factors**_
+_**Predisposing factors:**_
 Sociodemographic factors included age, sex, country of residence, educational level, and the (estimated) age(s) of their housemate(s).
@@
 
-_**COVID-19 preventive measures**_
+_**COVID-19 preventive measures:**_
 Participants were asked, “During the past 7 days, have you been observing any of the following preventive measures against COVID-19?
@@
 
-_**Enabling factors**_
+_**Enabling factors:**_
 Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel[@Bono].
 
-_**Need for care factors**_ include two questions on 1) the level of fear/worry of being infected with COVID-19 (ranging from 1=not at all worried to 5=extremely worried), and 2) having been quarantined (either at home or elsewhere) at any point in time during the COVID-19 epidemic.
+_**Need for care factors:**_ include two questions on 1) the level of fear/worry of being infected with COVID-19 (ranging from 1=not at all worried to 5=extremely worried), and 2) having been quarantined (either at home or elsewhere) at any point in time during the COVID-19 epidemic.
 
-_**Data analysis**_
+_**Data analysis procedure**_
 
@@
 
-## Data aquisition
-_As applicable, explain where and how you got the data. If you directly import the data from an online source, you can combine this section with the next._
-
-## Data import and cleaning_ html_document
+## Data Analysis:
 ---
+First of all, let's have a look at the overall descriptive status of the participants.
 ```{r}
 library(here)
-```
-## Exploratory analysis
-
-```{r summarytable,  echo=FALSE}
 resulttable=readRDS("../../results/Overall.rds")
@@
 ```
-
-As the infection status information of the participants is the main outcome variable, let's see its distribution among the participants:
-
-```{r resultfigure,  fig.cap='Infection Status Information.', echo=FALSE}
-knitr::include_graphics("../../results/infection_status_info_distribution.png")
-```
-
 Among the participants, **78.9%** are less than or equal  to 35 years old.
 That indicates that majority of the participants tend to be younger.
-While **45.18%** of the participants were female, **54.82%** were male, which shows less chance of biad due to sex.
+While **45.18%** of the participants were female, **54.82%** were male, which shows less chance of bias due to sex.
 **78.05%** of the participants had a bachelor or post-bachelor degree, clearly indicating that majority of the participants had pretty good education background.
@@
 Only **22%** of the participants recorded to have some sort of chronic disease.
-**(Separate analysis for each variable was done and the data can be accessed/viewd through the "supplementary.rmd" file)**
+**(Separate analysis for each variable was done and the data can be accessed/viewed through the "supplementary.rmd" file)**
 
-Let's look at the logistic regression analysis and its statistics summary between the **outcome variable** (infection status info) and the three key **predisposing factors** (Age, Sex, Education level).
+As the infection status information of the participants is the _**main outcome variable**_, let's see its distribution among the participants:
+
+```{r resultfigure,  fig.cap='Infection Status Information.', echo=FALSE}
+knitr::include_graphics("../../results/infection_status_info_distribution.png")
+```
+So, among 759 participants, 445 didn't have any test.
+197 was tested positive and 64 was tested negative.
+Clearly, there is major difference in number between the group who have gone through testing and who haven't.
+Our main focus is to find out which factors are affecting their decision whether they want to get tested or not.
+
+Let's look at the univariate logistic regression analysis and its statistics summary between the **outcome variable** (infection status info) and the three key **predisposing factors** (Age, Sex, Education level).
 ```{r summarytable12,  echo=FALSE}
@@
 ```
+
+Here, all three predisposing factors (Age, Sex and Education level) seems to have a significant effect on the participants' decision making to get tested or not as the p-values are <0.05.
+The quality of this model selection has been supported by the statistical data shown below:
 
@@
 
-Next, we want to see the logistic regression analysis statistics between the **outcome variable** (infection status info) and the three key **enabling factors** (socio economic status, area of residence,student/healthworker, source of covid news).
+Next, we want to see the univariate logistic regression analysis statistics between the **outcome variable** (infection status info) and the three key **enabling factors** (socio economic status, area of residence,student/healthworker, source of covid news).
 
@@
 ```
+
+While, difeerent socio economic status and residence area have strong importance on the testing decision making, the source of their covid information didn't seem to affect their decision making much.
+The quality of this model selection has been supported by the statistical data shown below:
 
@@
 ```
+
+Their worry level seems to have affect their decision to get tested for covid.The quality of this model selection has been supported by the statistical data shown below:
 
@@
 
-## Summary and Interpretation
-_Summarize what you did, what you found and what it means._
+## Results
+
+In total, 759 participants were included in the study with mean age 30.70 years. Of these 63% had never tested for COVID-19, 28% tested positive and 9.0% tested negative
+
+**Predisposing factor**
+
+One in five participants (20.1%) were 35 years and older, 45.18% were female, 78% had a graduate/postgraduate education, 21.5% had at least one diagnosed chronic/underlying disease, and only 2.1% did not adhere to the any of the four COVID-19 preventive measures.
+
+**Enabling/disabling factors**
+
+Most participants (63.03%) resided in urban areas, 56.0% rated their socio-economic status as upper middle to high-income, and 32% were students or workers in health care.
+The most trusted source of COVID-19 information/advice was health care personnel (33.5%), 37% had correct COVID-19 knowledge, and 46% reported moderate to severe psychological distress.
+
+**Need for care factors**
+
+More than half of the participants (70.7%) were very or extremely worried about being (re)infected with COVID-19, and 57.64% had been quarantined during the COVID-19 pandemic (see Table 1 and exploratory.rmd).
+
+**Associations**
+
+In the logistic regression model, predisposing factors (Age, Sex, Education Level) and enabling/disabling factors (urban residence, higher perceived economic status, being a student or worker in the health care sector) increased the odds of COVID-19 testing.Also, multivariate logistic regression of the odds of a COVID-19 positive diagnosis among all individuals tested or not tested found that urban residence, higher perceived economic status were positively associated with a COVID-19 positive diagnosis.
 

### 2021-12-10 products/manuscript/supplementary.Rmd
Final update!

@@
 
+**###I wanted to see the age distribution of the participants.**
 ```{r summarytable,  echo=FALSE}
@@
 ```
-**78.9% of total participants are less than or equal  to 35 years old.**
+_78.9% of total participants are less than or equal  to 35 years old._
 
+**###Next, I wanted to see the gender distribution of the participants**
 ```{r summarytable2,  echo=FALSE}
@@
 ```
-**While 45.18% of the participants were female, 54.82% were male.**
+_While 45.18% of the participants were female, 54.82% were male._
 
+**###here, I wanted to see which education background each of the participants possessed**
 ```{r summarytable3,  echo=FALSE}
@@
 ```
-**78.05% of the participants had a bachelor or post-bachelor degree**
+_78.05% of the participants had a bachelor or post-bachelor degree_
+
+**###Now, I want to see which income group each of them belong to**
 ```{r summarytable4,  echo=FALSE}
@@
 ```
-**Almost 50% of the participants belongs to "upper middle income category"**
+_Almost 50% of the participants belongs to "upper middle income category"_
+
+**###Where do they live?**
 ```{r summarytable5,  echo=FALSE}
@@
 ```
-**Less than 10% of the participants live in a village/rural area**
+_Less than 10% of the participants live in a village/rural area_
+
+**###Let's see which source they have been using to get updates about covid**
 ```{r summarytable6,  echo=FALSE}
@@
 ```
-**Health professionals and Tv/radio seems to be the most trusted source to the participants.**
+_Health professionals and Tv/radio seems to be the most trusted source to the participants._
+
+**###Are most of them working from home or not? Let's find out**
 ```{r summarytable7,  echo=FALSE}
@@
 ```
-**Apparently equal half of the participants worked from or not**
+_Apparently equal half of the participants worked from or not_
+
+**###I wanted to see what proportion of the participants had to undergo quarantine at some stages**
 ```{r summarytable8,  echo=FALSE}
@@
 ```
-**Major half of the participants did quarantine at some stage during the study**
+_Major half of the participants did quarantine at some stage during the study_
+
+**###What proportion of the participants knew their infection status (positive/negative/no test doen)? This is our primary outcome of interest. So, fiinding this was very important**
 ```{r summarytable9,  echo=FALSE}
@@
 ```
-**63% of the participants didn't go through a COVID test**
+_63% of the participants didn't go through a COVID test._
+
+**###What was the worry level of the participants?
+We divided the cohort in groupd like 'moderrately worried', 'a little worried', 'very worried', 'extremely worried' and 'not at all worried'.
+Proportion for each group is shown below:**
 ```{r summarytable10,  echo=FALSE}
@@
 ```
-**Almost half of the participants (46%) were moderate or more worried about reinfection**
+_Almost half of the participants (46%) were moderate or more worried about reinfection_
+
+**###What percent of participants had some sort of chronic disease history? Let's find out**
 ```{r summarytable11,  echo=FALSE}
@@
 ```
-**Only 22% of the participants recorded to have some sort of chronic disease**
+_Only 22% of the participants recorded to have some sort of chronic disease_
